# Initialize
## Set Options
```{r purl = TRUE}
# Toggle purl = FALSE to run model-nowcasts-backtest.rmd and purl = TRUE to run windows task scheduler
DIR = 'D:/Onedrive/__Projects/econforecasting'
M1_PATH = 'D:/Onedrive/__Projects/econforecasting/model-outputs/[2021-07-14] m1.rds'
PACKAGE_DIR = 'D:/Onedrive/__Projects/econforecasting/r-package' # Path to package with helper functions
INPUT_DIR = 'D:/Onedrive/__Projects/econforecasting/model-inputs' # Path to directory with constants.r (SQL DB info, SFTP info, etc.)
OUTPUT_DIR = 'D:/Onedrive/__Projects/econforecasting/model-outputs'
```

# Initialize
```{r}
# General purpose
library(tidyverse) # General
library(data.table) # General
library(devtools) # General
library(lubridate) # Dates
library(glue) # String Interpolation
# Data parse/import
library(jsonlite) # JSON Parser
library(rvest) # HTML Parser
library(httr) # CURL Interface
# SQL/Apache Spark
library(DBI) # SQL Interface
# library(RPostgres) # PostgreSQL
# library(rsparklyr) # Spark
# My package
devtools::load_all(path = PACKAGE_DIR)
devtools::document(PACKAGE_DIR)
# library(econforecasting)

# Set working directory
setwd(DIR)

# Read constants
source(file.path(INPUT_DIR, 'constants.r'))
```

## Load RDS
```{r}
local({
	
	rds = readRDS(M1_PATH)

	p <<- rds$p
	m <<- rds$m
	h <<- rds$h
})
```


# Nowcast

## Get dates
```{r}
local({
	
	quartersForward = 1
	
	pcaVarnames = p$variablesDf %>% dplyr::filter(., nc_dfm_input == TRUE) %>% .$varname
	
	pcaVariablesDf =
		h$st$m %>%
		dplyr::select(., date, all_of(pcaVarnames)) %>%
		dplyr::filter(., date >= as.Date('2010-01-01'))
	
	bigTDates = pcaVariablesDf %>% dplyr::filter(., !if_any(everything(), is.na)) %>% .$date
	bigTauDates = pcaVariablesDf %>% dplyr::filter(., if_any(everything(), is.na)) %>% .$date
	bigTStarDates =
		bigTauDates %>%
		tail(., 1) %>%
		seq(
			from = .,
			to =
				# Get this quarter
				econforecasting::strdateToDate(paste0(lubridate::year(.), 'Q', lubridate::quarter(.))) %>%
				# Get next quarter minus a month
				lubridate::add_with_rollback(., months(3 * (1 + quartersForward) - 1)),
			by = '1 month'
			) %>%
		.[2:length(.)]
	
	
	bigTDate = tail(bigTDates, 1)
	bigTauDate = tail(bigTauDates, 1)
	bigTStarDate = tail(bigTauDates, 1)
	
	bigT = length(bigTDates)
	bigTau = bigT + length(bigTauDates)
	bigTStar = bigTau + length(bigTStarDates)
	
	timeDf =
		tibble(
			date = as.Date(c(pcaVariablesDf$date[[1]], bigTDate, bigTauDate, bigTStarDate)),
			time = c('1', 'T', 'Tau', 'T*')
		)
	
	

	m$nc$pcaVariablesDf <<- pcaVariablesDf
	m$nc$pcaVarnames <<- pcaVarnames
	m$nc$quartersForward <<- quartersForward
	m$nc$bigTDates <<- bigTDates
	m$nc$bigTauDates <<- bigTauDates
	m$nc$bigTStarDates <<- bigTStarDates
	m$nc$bigTDate <<- bigTDate
	m$nc$bigTauDate <<- bigTauDate
	m$nc$bigTStarDate <<- bigTStarDate
	m$nc$bigT <<- bigT
	m$nc$bigTau <<- bigTau
	m$nc$bigTStar <<- bigTStar
	m$nc$timeDf <<- timeDf
})
```

## Extract factors
```{r}
local({
	
	xDf = m$nc$pcaVariablesDf %>% dplyr::filter(., date %in% m$nc$bigTDates)
	
	xMat =
		xDf %>%
		dplyr::select(., -date) %>%
		as.matrix(.) %>%
		scale(.)
	
	lambdaHat = eigen(t(xMat) %*% xMat) %>% .$vectors
	fHat = (xMat) %*% lambdaHat
	bigN = ncol(xMat)
	bigT = nrow(xMat)
	bigCSquared = min(bigN, bigT)
	
	# Total variance of data
	totalVar = xMat %>% cov(.) %>% diag(.) %>% sum(.)
	
	# Calculate ICs from Bai and Ng (2002)
	# Total SSE should be approx 0 due to normalization above;
	# sapply(1:ncol(xMat), function(i)
	# 	sapply(1:nrow(xMat), function(t)
	# 		(xMat[i, 1] - matrix(lambdaHat[i, ], nrow = 1) %*% matrix(fHat[t, ], ncol = 1))^2
	# 		) %>% sum(.)
	# 	) %>%
	# 	sum(.) %>%
	# 	{./(ncol(xMat) %*% nrow(xMat))}
	(xMat - (fHat %*% t(lambdaHat)))^1
	
	# Now test by R
	mseByR =
		sapply(1:bigN, function(r)
			sum((xMat - (fHat[, 1:r, drop = FALSE] %*% t(lambdaHat)[1:r, , drop = FALSE]))^2)/(bigT * bigN)
			)
	
	
	# Explained variance of data
	screeDf =
		fHat %>% cov(.) %>% diag(.) %>%
		{lapply(1:length(.), function(i)
			tibble(
				factors = i,
				var_explained_by_factor = .[i],
				pct_of_total = .[i]/totalVar,
				cum_pct_of_total = sum(.[1:i])/totalVar
				)
			)} %>%
		dplyr::bind_rows(.) %>%
		dplyr::mutate(., mse = mseByR) %>%
		dplyr::mutate(
			.,
			ic1 = (mse) + factors * (bigN + bigT)/(bigN * bigT) * log((bigN * bigT)/(bigN + bigT)),
			ic2 = (mse) + factors * (bigN + bigT)/(bigN * bigT) * log(bigCSquared),
			ic3 = (mse) + factors * (log(bigCSquared)/bigCSquared)
		)
	
	screePlot =
		screeDf %>%
    	ggplot(.) +
    	geom_col(aes(x = factors, y = cum_pct_of_total, fill = factors)) +
		# geom_col(aes(x = factors, y = pct_of_total)) +
    	labs(title = 'Percent of Variance Explained', x = 'Factors (R)', y = 'Cumulative % of Total Variance Explained', fill = NULL) + 
    	ggthemes::theme_fivethirtyeight()

	
	bigR =
		screeDf %>%
		dplyr::filter(., ic1 == min(ic1)) %>%
		.$factors + 1
		# ((
		# 	{screeDf %>% dplyr::filter(cum_pct_of_total >= .80) %>% head(., 1) %>%.$factors} +
		#   	{screeDf %>% dplyr::filter(., ic1 == min(ic1)) %>% .$factors}
		# 	)/2) %>%
		# round(., digits = 0)
	
	zDf =
		xDf[, 'date'] %>%
		dplyr::bind_cols(
			.,
			fHat[, 1:bigR] %>% as.data.frame(.) %>% setNames(., paste0('f', 1:bigR))
			)
	

	zPlots =
		purrr::imap(colnames(zDf) %>% .[. != 'date'], function(x, i)
			dplyr::select(zDf, all_of(c('date', x))) %>%
				setNames(., c('date', 'value')) %>%
				ggplot() +
				geom_line(
					aes(x = date, y = value),
					color = hcl(h = seq(15, 375, length = bigR + 1), l = 65, c = 100)[i]
					) +
				labs(x = NULL, y = NULL, title = paste0('Estimated PCA Factor ', str_sub(x, -1), ' Plot')) +
				ggthemes::theme_fivethirtyeight() +
				scale_x_date(date_breaks = '1 year', date_labels = '%Y')
			)
	
	factorWeightsDf =
		lambdaHat %>%
		as.data.frame(.) %>% 
		as_tibble(.) %>%
		setNames(., paste0('f', str_pad(1:ncol(.), pad = '0', 1))) %>%
		dplyr::bind_cols(weight = colnames(xMat), .) %>%
		tidyr::pivot_longer(., -weight, names_to = 'varname') %>%
		dplyr::group_by(varname) %>%
		dplyr::arrange(., varname, desc(abs(value))) %>%
		dplyr::mutate(., order = 1:n(), valFormat = paste0(weight, ' (', round(value, 2), ')')) %>%
		dplyr::ungroup(.) %>%
		dplyr::select(., -value, -weight) %>%
		tidyr::pivot_wider(., names_from = varname, values_from = valFormat) %>%
		dplyr::arrange(., order) %>%
		dplyr::select(., -order) %>%
		dplyr::select(., paste0('f', 1:bigR))
	
	
	m$nc$factorWeightsDf <<- factorWeightsDf
	m$nc$screeDf <<- screeDf
	m$nc$screePlot <<- screePlot
	m$nc$bigR <<- bigR
	m$nc$pcaInputDf <<- xDf
	m$nc$zDf <<- zDf
	m$nc$zPlots <<- zPlots
})
```

## Run as VAR(1)
```{r}
local({
	
	inputDf =
		m$nc$zDf %>%
    	econforecasting::addLags(., 1, TRUE) %>%
		na.omit(.) #%>%
		# dplyr::filter(., date <= '2020-02-01' | date >= '2020-09-01')
	
	yMat = inputDf %>% dplyr::select(., -contains('.l'), -date) %>% as.matrix(.)
	xDf = inputDf %>% dplyr::select(., contains('.l')) %>% dplyr::bind_cols(constant = 1, .)
	
	# solve(t(xMat) %*% xMat) %*% (t(xMat) %*% yMat)
	coefDf =
		lm(yMat ~ . - 1, data = xDf) %>%
		coef(.) %>%
		as.data.frame(.) %>%
		rownames_to_column(., 'coefname') %>%
		as_tibble(.) 
	
	gofDf =
		lm(yMat ~ . - 1, xDf) %>%
		resid(.) %>%
		as.data.frame(.) %>%
		as_tibble(.) %>%
		tidyr::pivot_longer(., everything(), names_to = 'varname') %>%
		dplyr::group_by(., varname) %>%
		dplyr::summarize(., MAE = mean(abs(value)), MSE = mean(value^2))

	residPlot =
		lm(yMat ~ . - 1, xDf) %>%
	    resid(.) %>%
	    as.data.frame(.) %>%
	    as_tibble(.) %>%
	    dplyr::bind_cols(date = inputDf$date, .) %>%
		tidyr::pivot_longer(., -date) %>%
		ggplot(.) + 	
		geom_line(aes(x = date, y = value, group = name, color = name), size = 1) +
		labs(title = 'Residuals plot for PCA factors', x = NULL, y = NULL, color = NULL) +
		ggthemes::theme_fivethirtyeight()
	
	fittedPlots =
		lm(yMat ~ . - 1, data = xDf) %>%
    	fitted(.) %>%
		as_tibble(.) %>%
		dplyr::bind_cols(date = inputDf$date, ., type = 'Fitted Values') %>%
		dplyr::bind_rows(., m$nc$zDf %>% dplyr::mutate(., type = 'Data')) %>%
		tidyr::pivot_longer(., -c('type', 'date')) %>% 
		as.data.table(.) %>%
		split(., by = 'name') %>%
		purrr::imap(., function(x, i)
			ggplot(x) +
				geom_line(
					aes(x = date, y = value, group = type, linetype = type, color = type),
					size = 1, alpha = 1.0
					) +
				labs(
					x = NULL, y = NULL, color = NULL, linetype = NULL,
					title = paste0('Fitted values vs actual for factor ', i)
					) +
				scale_x_date(date_breaks = '1 year', date_labels = '%Y') +
				ggthemes::theme_fivethirtyeight()
			)
	
	bMat = coefDf %>% dplyr::filter(., coefname != 'constant') %>% dplyr::select(., -coefname) %>% t(.)
	cMat = coefDf %>% dplyr::filter(., coefname == 'constant') %>% dplyr::select(., -coefname) %>% t(.)
	qMat =
		lm(yMat ~ . - 1, data = xDf) %>%
	    residuals(.) %>% 
		as_tibble(.) %>%
		purrr::transpose(.) %>%
		lapply(., function(x) as.numeric(x)^2 %>% diag(.)) %>%
		{purrr::reduce(., function(x, y) x + y)/length(.)}
	
	
	m$nc$varFittedPlots <<- fittedPlots
	m$nc$varResidPlot <<- residPlot
	m$nc$varGofDf <<- gofDf
	m$nc$varCoefDf <<- coefDf
	m$nc$qMat <<- qMat 
	m$nc$bMat <<- bMat
	m$nc$cMat <<- cMat
})
```


## Run DFM on monthly variables included in PCA
```{r}
local({
	
	yMat = m$nc$pcaInputDf %>% dplyr::select(., -date) %>% as.matrix(.)
	xDf = m$nc$zDf %>% dplyr::select(., -date) %>% dplyr::bind_cols(constant = 1, .)
	
	coefDf =
		lm(yMat ~ . - 1, xDf) %>%
		coef(.) %>%	
		as.data.frame(.) %>%
    	rownames_to_column(., 'coefname') %>%
		as_tibble(.)
	
	
	fittedPlots =
		lm(yMat ~ . - 1, xDf) %>%
	    fitted(.) %>%
	    as_tibble(.) %>%
	    dplyr::bind_cols(date = m$nc$zDf$date, ., type = 'Fitted Values') %>%
	    dplyr::bind_rows(., m$nc$pcaInputDf %>% dplyr::mutate(., type = 'Data')) %>%
		tidyr::pivot_longer(., -c('type', 'date')) %>%
		as.data.table(.) %>%
		split(., by = 'name') %>%
		purrr::imap(., function(x, i)
        	ggplot(x) +
	            geom_line(
	                aes(x = date, y = value, group = type, linetype = type, color = type),
	                size = 1, alpha = 1.0
	            ) +
	            labs(
	                x = NULL, y = NULL, color = NULL, linetype = NULL,
	                title = paste0('Fitted values vs actual for factor ', i)
	            ) +
	            scale_x_date(date_breaks = '1 year', date_labels = '%Y') +
	            ggthemes::theme_fivethirtyeight()
	    )
		
	
	gofDf =
		lm(yMat ~ . - 1, xDf) %>%
		resid(.) %>%
		as.data.frame(.) %>%
		as_tibble(.) %>%
		tidyr::pivot_longer(., everything(), names_to = 'varname') %>%
		dplyr::group_by(., varname) %>%
		dplyr::summarize(., MAE = mean(abs(value)), MSE = mean(value^2))
	
	
	aMat = coefDf %>% dplyr::filter(., coefname != 'constant') %>% dplyr::select(., -coefname) %>% t(.)
	dMat = coefDf %>% dplyr::filter(., coefname == 'constant') %>% dplyr::select(., -coefname) %>% t(.)

	rMat0 =
		lm(yMat ~ . - 1, data = xDf) %>%
	    residuals(.) %>% 
		as_tibble(.) %>%
		purrr::transpose(.) %>%
		lapply(., function(x) as.numeric(x)^2 %>% diag(.)) %>%
		{purrr::reduce(., function(x, y) x + y)/length(.)}
	
	rMatDiag = tibble(varname = m$nc$pcaVarnames, variance = diag(rMat0))

	
	rMats =
		lapply(m$nc$bigTauDates, function(d)
			sapply(m$nc$pcaVarnames, function(v)
				h$st$m %>%
					dplyr::filter(., date == (d)) %>%
					.[[v]] %>% 
					{if (is.na(.)) 1e20 else dplyr::filter(rMatDiag, varname == v)$variance}
				) %>%
				diag(.)
			) %>%
		c(lapply(1:length(m$nc$bigTDates), function(x) rMat0), .)

	
	m$nc$dfmGofDf <<- gofDf
	m$nc$dfmCoefDf <<- coefDf
	m$nc$dfmFittedPlots <<- fittedPlots
	m$nc$rMats <<- rMats
	m$nc$aMat <<- aMat
	m$nc$dMat <<- dMat
})
```

## Compute Kalman filter
```{r}
local({
	
	bMat = m$nc$bMat
	cMat = m$nc$cMat
	aMat = m$nc$aMat
	dMat = m$nc$dMat
	rMats = m$nc$rMats
	qMat = m$nc$qMat
	yMats =
		dplyr::bind_rows(
			m$nc$pcaInputDf,
			h$st$m %>%
				dplyr::filter(., date %in% m$nc$bigTauDates) %>%
				dplyr::select(., date, m$nc$pcaVarnames)
			) %>%
		dplyr::mutate(., across(-date, function(x) ifelse(is.na(x), 0, x))) %>%
		dplyr::select(., -date) %>%
		purrr::transpose(.) %>%
		lapply(., function(x) matrix(unlist(x), ncol = 1))

	z0Cond0 = matrix(rep(0, m$nc$bigR), ncol = 1)
	sigmaZ0Cond0 = matrix(rep(0, m$nc$bigR^2), ncol = m$nc$bigR)
		
	zTCondTMinusOne = list()
	zTCondT = list()
	
	sigmaZTCondTMinusOne = list()
	sigmaZTCondT = list()
	
	yTCondTMinusOne = list()
	sigmaYTCondTMinusOne = list()
	
	pT = list()

	for (t in 1:length(c(m$nc$bigTDates, m$nc$bigTauDates))) {
		# message(t)
		# Prediction Step
		zTCondTMinusOne[[t]] = bMat %*% {if (t == 1) z0Cond0 else zTCondT[[t-1]]} + cMat
		sigmaZTCondTMinusOne[[t]] = bMat %*% {if (t == 1) sigmaZ0Cond0 else sigmaZTCondT[[t-1]]} + qMat
		yTCondTMinusOne[[t]] = aMat %*% zTCondTMinusOne[[t]] + dMat
		sigmaYTCondTMinusOne[[t]] = aMat %*% sigmaZTCondTMinusOne[[t]] %*% t(aMat) + rMats[[t]]
		
		# Correction Step
		pT[[t]] = sigmaZTCondTMinusOne[[t]] %*% t(aMat) %*%
			{
				if (t %in% 1:length(m$nc$bigTDates)) solve(sigmaYTCondTMinusOne[[t]])
				else chol2inv(chol(sigmaYTCondTMinusOne[[t]]))
				}
		zTCondT[[t]] = zTCondTMinusOne[[t]] + pT[[t]] %*% (yMats[[t]] - yTCondTMinusOne[[t]])
		sigmaZTCondT[[t]] = sigmaZTCondTMinusOne[[t]] - (pT[[t]] %*% sigmaYTCondTMinusOne[[t]] %*% t(pT[[t]]))
	}
	
	
	kFitted =
		zTCondT %>%
		purrr::map_dfr(., function(x)
			as.data.frame(x) %>% t(.) %>% as_tibble(.)
			) %>%
		dplyr::bind_cols(date = c(m$nc$bigTDates, m$nc$bigTauDates), .) 
	
	
	## Smoothing step
	zTCondBigTSmooth = list()
	sigmaZTCondBigTSmooth = list()
	sT = list()
	
	for (t in (length(zTCondT) - 1): 1) {
		# message(t)
		sT[[t]] = sigmaZTCondT[[t]] %*% t(bMat) %*% solve(sigmaZTCondTMinusOne[[t + 1]])
		zTCondBigTSmooth[[t]] = zTCondT[[t]] + sT[[t]] %*% 
			({if (t == length(zTCondT) - 1) zTCondT[[t + 1]] else zTCondBigTSmooth[[t + 1]]} - zTCondTMinusOne[[t + 1]])
		sigmaZTCondBigTSmooth[[t]] = sigmaZTCondT[[t]] - sT[[t]] %*%
			(sigmaZTCondTMinusOne[[t + 1]] -
			 	{if (t == length(zTCondT) - 1) sigmaZTCondT[[t + 1]] else sigmaZTCondBigTSmooth[[t + 1]]}
			 ) %*% t(sT[[t]])
	}
	
	kSmooth =
		zTCondBigTSmooth %>%
		purrr::map_dfr(., function(x)
			as.data.frame(x) %>% t(.) %>% as_tibble(.)
			) %>%
		dplyr::bind_cols(date = c(m$nc$bigTDates, m$nc$bigTauDates) %>% .[1:(length(.) - 1)], .) 
	
	
	
	
	## Forecasting step
	zTCondBigT = list()
	sigmaZTCondBigT = list()
	yTCondBigT = list()
	sigmaYTCondBigT = list()
	
	for (j in 1:length(m$nc$bigTStarDates)) {
		zTCondBigT[[j]] = bMat %*% {if (j == 1) zTCondT[[length(zTCondT)]] else zTCondBigT[[j - 1]]} + cMat
		sigmaZTCondBigT[[j]] = bMat %*% {if (j == 1) sigmaZTCondT[[length(sigmaZTCondT)]] else sigmaZTCondBigT[[j - 1]]} + qMat
		yTCondBigT[[j]] = aMat %*% zTCondBigT[[j]] + dMat
		sigmaYTCondBigT[[j]] = aMat %*% sigmaZTCondBigT[[j]] %*% t(aMat) + rMats[[1]]
	}
	
	kForecast =
		zTCondBigT %>%
		purrr::map_dfr(., function(x)
			as.data.frame(x) %>% t(.) %>% as_tibble(.)
			) %>%
		dplyr::bind_cols(date = m$nc$bigTStarDates, .)
	

	
	# Plot and Cleaning
	kfPlots =
		lapply(colnames(m$nc$zDf) %>% .[. != 'date'], function(.varname)
			dplyr::bind_rows(
				dplyr::mutate(m$nc$zDf, type = 'Data'),
				dplyr::mutate(kFitted, type = 'Kalman Filtered'),
				dplyr::mutate(kForecast, type = 'Forecast'),
				dplyr::mutate(kSmooth, type = 'Kalman Smoothed'),
				) %>%
				tidyr::pivot_longer(., -c('date', 'type'), names_to = 'varname') %>%
				dplyr::filter(., varname == .varname) %>%
				ggplot(.) +
				geom_line(aes(x = date, y = value, color = type), size = 1) + 
				labs(x = NULL, y = NULL, color = NULL, title = paste0('Kalman smoothed values for ', .varname)) +
	            scale_x_date(date_breaks = '1 year', date_labels = '%Y') +
				ggthemes::theme_fivethirtyeight()
			)
	
	
	fDf =
		dplyr::bind_rows(
			kSmooth,
			tail(kFitted, 1),
			kForecast #%>% dplyr::mutate(., f1 = mean(dplyr::filter(m$nc$zDf, date < '2020-03-01')$f1))
			)
	
	yDf =
		yTCondBigT %>%
		purrr::map_dfr(., function(x) as_tibble(t(as.data.frame(x)))) %>%
		dplyr::bind_cols(date = m$nc$bigTStarDates, .)
	
	kfDf = yDf
		# yDf %>%
		# dplyr::select(
		# 	.,
		# 	date#,
		# 	#all_of(dplyr::filter(m$paramsDf, nowcast == 'kf')$varname)
		# 	)
	
	m$nc$fDf <<- fDf
	m$nc$kfPlots <<- kfPlots
	m$nc$yDf <<- yDf
	m$nc$kfDf <<- kfDf
})
```

## Add baseline forecasts from other page
```{r}
local({
  
	# d1 form MUST match stationary form for these variables
# 	reqs =
# 		tribble(
# 			~fcname, ~varname,
# 			'dns', 't10y',
# 			'dns', 't30y',
# 			'dns', 't05y',
# 			'dns', 't02y',
# 			'dns', 't01y',
# 			'dns', 't06m',
# 			'dns', 't03m',
# 			'dns', 't01m',
# 			'dns', 't20y',
# 			'dns', 't07y',
# 			'cme', 'ffr',
# 			'cme', 'sofr'
# 			)
# 	
# 	cmefiDf =
# 		dplyr::bind_rows(m$ext$sources) %>%
# 		dplyr::filter(., form == 'd1') %>%
# 		dplyr::select(., -form) %>%
# 		dplyr::right_join(., reqs, by = c('fcname', 'varname')) %>%
# 		dplyr::group_by(., varname) %>%
# 		dplyr::filter(., vdate == max(vdate)) %>%
# 		dplyr::ungroup(.) %>%
# 		dplyr::select(., -vdate, -fcname) %>%
# 		dplyr::mutate(., freq = 'm') %>%
# 		# Only keep rows without a match in FRED data
# 		dplyr::anti_join(., h$flatDf %>% dplyr::filter(., form == 'd1'), by = c('varname', 'date', 'freq')) %>%
# 		# Pivot
# 		dplyr::select(., -freq) %>%
# 		tidyr::pivot_wider(., names_from = varname, values_from = value) %>%
# 		dplyr::arrange(., date) %>%
# 		dplyr::filter(., date <= tail(m$nc$bigTStarDates, 1))
# 	
# 	
#   m$nc$cmefiDf <<- cmefiDf
})
```

## Forecast dfm.m monthly variables
```{r}
local({
	
	dfmVarnames = p$variablesDf %>% dplyr::filter(., nc_method == 'dfm.m') %>% .$varname
	
	dfmMDf = 
		lapply(dfmVarnames, function(.varname) {
			inputDf =
				dplyr::inner_join(
					m$nc$fDf,
					dplyr::select(h$st$m, date, all_of(.varname)),
					by = 'date'
				) %>%
				na.omit(.)

			yMat = dplyr::select(inputDf, all_of(.varname)) %>% as.matrix(.)
			xDf = dplyr::select(inputDf, -date, -all_of(.varname)) %>% dplyr::mutate(., constant = 1)

			coefDf =
				lm(yMat ~ . - 1, xDf)$coef %>%
	    		as.data.frame(.) %>% rownames_to_column(., 'coefname')	%>% as_tibble(.) %>%
				setNames(., c('coefname', 'value'))

			# Forecast dates + last historical date
			forecastDf0 =
				tibble(
					date = seq(from = tail(inputDf$date, 1), to = tail(m$nc$bigTStarDates, 1), by = '1 month')
					) %>%
				.[2:nrow(.), ] %>%
				dplyr::mutate(., !!.varname := 0) %>%
				dplyr::left_join(., m$nc$fDf, by = 'date') %>%
				dplyr::bind_cols(., constant = 1)

			forecastDf =
				purrr::reduce(1:nrow(forecastDf0), function(accum, x) {
					accum[x, .varname] =
						accum[x, ] %>%
						dplyr::select(., coefDf$coefname) %>%
						matrix(., ncol = 1) %>%
						{matrix(coefDf$value, nrow = 1) %*% as.numeric(.)}

					return(accum)
				}, .init = forecastDf0) %>%
				dplyr::select(., all_of(c('date', .varname)))
# 
# 			inputDf =
# 				dplyr::inner_join(
# 				m$nc$fDf,
# 				dplyr::select(m$h$m$st, date, all_of(.varname)) %>%
# 					econforecasting::addLags(., 1, .zero = TRUE),
# 				by = 'date'
# 				) %>%
# 				na.omit(.)
# 			
# 			yMat = dplyr::select(inputDf, all_of(.varname)) %>% as.matrix(.)
# 			xDf = dplyr::select(inputDf, -date, -all_of(.varname)) %>% dplyr::mutate(., constant = 1)
# 			
# 			coefDf =
# 				lm(yMat ~ . - 1, xDf)$coef %>%
# 	    		as.data.frame(.) %>% rownames_to_column(., 'coefname')	%>% as_tibble(.) %>%
# 				setNames(., c('coefname', 'value'))
# 			
# 			# Forecast dates + last historical date
# 			forecastDf0 =
# 				tibble(
# 					date = seq(from = tail(inputDf$date, 1), to = tail(m$nc$bigTStarDates, 1), by = '1 month')
# 					) %>%
# 				dplyr::mutate(., !!.varname := c(inputDf[[paste0(.varname, '.l1')]][[1]], rep(NA, nrow(.) - 1))) %>%
# 				dplyr::left_join(., m$nc$fDf, by = 'date') %>%
# 				dplyr::bind_cols(., constant = 1)
# 			
# 			forecastDf =
# 				purrr::reduce(2:nrow(forecastDf0), function(accum, x) {
# 					accum[x, .varname] =
# 						accum %>% econforecasting::addLags(., 1, .zero = TRUE) %>%
# 						.[x, ] %>%
# 						dplyr::select(., coefDf$coefname) %>%
# 						matrix(., ncol = 1) %>%
# 						{matrix(coefDf$value, nrow = 1) %*% as.numeric(.)}
# 					
# 					return(accum)
# 				}, .init = forecastDf0) %>%
# 				.[2:nrow(.), ] %>%
# 				dplyr::select(., all_of(c('date', .varname)))
		
			}) %>%
			purrr::reduce(., function(accum, x) dplyr::full_join(accum, x, by = 'date')) %>%
			dplyr::arrange(., date)


	m$nc$dfmMDf <<- dfmMDf	
})
```

## Forecast dfm.q quarterly variables w/elastic net
```{r}
local({
	
	dfmVarnames = p$variablesDf %>% dplyr::filter(., nc_method == 'dfm.q') %>% .$varname
	
	fDf =
		m$nc$fDf %>%
		tidyr::pivot_longer(., -date, names_to = 'varname') %>%
		dplyr::mutate(
			.,
			q = econforecasting::strdateToDate(paste0(lubridate::year(date), 'Q', lubridate::quarter(date)))
			) %>%
		dplyr::select(., -date) %>%
		dplyr::group_by(., varname, q) %>%
		dplyr::summarize(., value = mean(value), .groups = 'drop') %>%
		tidyr::pivot_wider(., names_from = varname, values_from = value) %>%
		dplyr::rename(., date = q)
	
	
	dfmRes =
		lapply(dfmVarnames %>% setNames(., .), function(.varname) {
			
	# 		inputDf =
	# 			dplyr::inner_join(
	# 				fDf,
	# 				dplyr::select(m$h$q$st, date, all_of(.varname)),
	# 				by = 'date'
	# 			) %>%
	# 			na.omit(.)
	# 
	# 		yMat = dplyr::select(inputDf, all_of(.varname)) %>% as.matrix(.)
	# 		xDf = dplyr::select(inputDf, -date, -all_of(.varname)) %>% dplyr::mutate(., constant = 1)
	# 
	# 		coefDf =
	# 			lm(yMat ~ . - 1, xDf)$coef %>%
	#     		as.data.frame(.) %>% rownames_to_column(., 'coefname')	%>% as_tibble(.) %>%
	# 			setNames(., c('coefname', 'value'))
	# 
	# 		# Forecast dates + last historical date
	# 		forecastDf0 =
	# 			tibble(
	# 				date = seq(from = tail(inputDf$date, 1), to = tail(m$nc$bigTStarDates, 1), by = '3 months')
	# 				) %>%
	# 			.[2:nrow(.), ] %>%
	# 			dplyr::mutate(., !!.varname := 0) %>%
	# 			dplyr::left_join(., m$nc$fDf, by = 'date') %>%
	# 			dplyr::bind_cols(., constant = 1)
	# 
	# 		forecastDf =
	# 			purrr::reduce(1:nrow(forecastDf0), function(accum, x) {
	# 				accum[x, .varname] =
	# 					accum[x, ] %>%
	# 					dplyr::select(., coefDf$coefname) %>%
	# 					matrix(., ncol = 1) %>%
	# 					{matrix(coefDf$value, nrow = 1) %*% as.numeric(.)}
	# 
	# 				return(accum)
	# 			}, .init = forecastDf0) %>%
	# 			dplyr::select(., all_of(c('date', .varname)))

			inputDf =
				dplyr::inner_join(
					fDf,
					dplyr::select(h$st$q, date, all_of(.varname)) %>%
						econforecasting::addLags(., 1, .zero = TRUE),
					by = 'date'
				) %>%
				na.omit(.)

			yMat = dplyr::select(inputDf, all_of(.varname)) %>% as.matrix(.)
			xDf = dplyr::select(inputDf, -date, -all_of(.varname)) %>% dplyr::mutate(., constant = 1)
			
			glmResult = lapply(c(1), function(.alpha) {
				cv =
					glmnet::cv.glmnet(
						x = xDf %>% dplyr::select(., -constant) %>% as.matrix(.),
						y = yMat,
						deviance = 'mae',
						alpha = .alpha,
						intercept = TRUE
					)
				tibble(alpha = .alpha, lambda = cv$lambda, mae = cv$cvm) %>%
				dplyr::mutate(., min_lambda_for_given_alpha = (mae == min(mae))) %>%
				return(.)
				}) %>%
				dplyr::bind_rows(.) %>%
				dplyr::mutate(., min_overall = (mae == min(mae)))

			glmOptim = glmResult %>% dplyr::filter(., min_overall == TRUE)

			cvPlot =
				glmResult %>%
				ggplot(.) +
				geom_line(aes(x = log(lambda), y = mae, group = alpha, color = alpha)) +
				geom_point(
					data = glmResult %>% dplyr::filter(., min_lambda_for_given_alpha == TRUE),
					aes(x = log(lambda), y = mae), color = 'red'
				) +
				geom_point(
					data = glmResult %>% dplyr::filter(., min_overall == TRUE),
					aes(x = log(lambda), y = mae), color = 'green'
				) +
				labs(
					x = 'log(Lambda)', y = 'MAE', color = 'alpha',
					title = 'Elastic Net Hyperparameter Fit',
					subtitle = 'Red = MAE Minimizing Lambda for Given Alpha;
					Green = MAE Minimizing (Lambda, Alpha) Pair'
					)
			
		
			glmObj =
				glmnet::glmnet(
					x = xDf %>% dplyr::select(., -constant) %>% as.matrix(.),
					y = yMat,
					alpha = glmOptim$alpha,
					lambda = glmOptim$lambda
				)
  
			coefMat = glmObj %>% coef(.) %>% as.matrix(.)
			
			coefDf =
				coefMat %>%
			    as.data.frame(.) %>%
			    rownames_to_column(., var = 'Covariate') %>%
			    setNames(., c('coefname', 'value')) %>%
				as_tibble(.) %>%
				dplyr::mutate(., coefname = ifelse(coefname == '(Intercept)', 'constant', coefname))

			
			# Standard OLS
	# 		coefDf =
	# 			lm(yMat ~ . - 1, xDf)$coef %>%
	#     		as.data.frame(.) %>% rownames_to_column(., 'coefname') %>% as_tibble(.) %>%
	# 			setNames(., c('coefname', 'value'))

			# Forecast dates + last historical date
			forecastDf0 =
				tibble(
					date = seq(from = tail(inputDf$date, 1), to = tail(m$nc$bigTStarDates, 1), by = '3 months')
					) %>%
				dplyr::mutate(., !!.varname := c(tail(inputDf[[.varname]], 1), rep(NA, nrow(.) - 1))) %>%
				dplyr::left_join(., m$nc$fDf, by = 'date') %>%
				dplyr::bind_cols(., constant = 1)

			forecastDf =
				purrr::reduce(2:nrow(forecastDf0), function(accum, x) {
					accum[x, .varname] =
						accum %>% econforecasting::addLags(., 1, .zero = TRUE) %>%
						.[x, ] %>%
						dplyr::select(., coefDf$coefname) %>%
						matrix(., ncol = 1) %>%
						{matrix(coefDf$value, nrow = 1) %*% as.numeric(.)}

					return(accum)
				}, .init = forecastDf0) %>%
				.[2:nrow(.), ] %>%
				dplyr::select(., all_of(c('date', .varname)))
			
			list(
				forecastDf = forecastDf,
				coefDf = coefDf,
				glmOptim = glmOptim,
				cvPlot = cvPlot
				)
			})
	
	
	glmCoefList = purrr::map(dfmRes, ~ .$coefDf) 
	
	glmOptimDf =
		purrr::imap_dfr(dfmRes, function(x, i)
			x$glmOptim %>% dplyr::bind_cols(varname = i, .)
			)
	
	cvPlots = purrr::map(dfmRes, ~ .$cvPlot)
	
	dfmDf =
		dfmRes %>%
		lapply(., function(x) x$forecastDf) %>%
		purrr::reduce(., function(accum, x) dplyr::full_join(accum, x, by = 'date')) %>%
		dplyr::arrange(., date)


	m$nc$glmCoefQList <<-glmCoefList 
	m$nc$glmOptimQDf <<- glmOptimDf
	m$nc$cvPlotsQ <<- cvPlots
	m$nc$dfmQDf <<- dfmDf
})
```


# Finalize Nowcasts

## Aggregate
```{r}
local({
	
	mDf = m$nc$dfmMDf
		# list(m$nc$dfmMDf, m$nc$cmefiDf) %>%
		# purrr::reduce(., function(x, y) dplyr::full_join(x, y, by = 'date')) %>%
		# dplyr::arrange(., date)
	
	qDf =
		list(m$nc$dfmQDf) %>%
		purrr::reduce(., function(x, y) dplyr::full_join(x, y, by = 'date')) %>%
		dplyr::arrange(., date)


	m$ncpred0$st$m <<- mDf
	m$ncpred0$st$q <<- qDf
})
```


## Detransform
```{r}
local({
	
		
	mDf =
		m$ncpred0$st$m %>%
		{lapply(colnames(.) %>% .[. != 'date'], function(.varname) {
			
			transform = dplyr::filter(p$variablesDf, varname == .varname)$st
			
			fcDf = dplyr::select(., date, .varname) %>% na.omit(.)
				
			histDf = tail(dplyr::filter(na.omit(h$base$m[, c('date', .varname)]), date < min(fcDf$date)), 1)
			
			fcDf %>%
				dplyr::mutate(
					.,
					!!.varname := 
						{
	                        if (transform == 'dlog') undlog(fcDf[[2]], histDf[[2]])
							else if (transform == 'apchg') unapchg(fcDf[[2]], 12, histDf[[2]])
							else if (transform == 'base') .[[2]]
							else stop('Err: ', .varname)
							}
						)
			
			})} %>%
		purrr::reduce(., function(x, y) dplyr::full_join(x, y, by = 'date')) %>%
		dplyr::arrange(., date)
	
	
	qDf =
		m$ncpred0$q$st %>%
		{lapply(colnames(.) %>% .[. != 'date'], function(.varname) {
			
			transform = dplyr::filter(p$variablesDf, varname == .varname)$st
			
			fcDf = dplyr::select(., date, .varname) %>% na.omit(.)
				
			histDf = tail(dplyr::filter(na.omit(h$base$q[, c('date', .varname)]), date < min(fcDf$date)), 1)
			
			fcDf %>%
				dplyr::mutate(
					.,
					!!.varname := 
						{
	                        if (transform == 'dlog') undlog(fcDf[[2]], histDf[[2]])
							else if (transform == 'apchg') unapchg(fcDf[[2]], 4, histDf[[2]])
							else if (transform == 'base') .[[2]]
							else stop('Err: ', .varname)
							}
						)
			
			})} %>%
		purrr::reduce(., function(x, y) dplyr::full_join(x, y, by = 'date')) %>%
		dplyr::arrange(., date)
		
	
	m$ncpred0$base$m <<- mDf
	m$ncpred0$base$q <<- qDf
})
```

## Calculate GDP nowcast
```{r}
local({
	
	qDf =
		m$ncpred0$q$base %>%
		dplyr::transmute(
			.,
			date,
			govt = govtf + govts,
			ex = exg + exs,
			im = img + ims,
			nx = ex - im,
			pdin = pdinstruct + pdinequip + pdinip,
			pdi = pdin + pdir + pceschange,
			pces = pceshousing + pceshealth + pcestransport + pcesrec + pcesfood + pcesfinal + pcesother + pcesnonprofit,
			pcegn = pcegnfood + pcegnclothing + pcegngas + pcegnother,
			pcegd = pcegdmotor + pcegdfurnish + pcegdrec + pcegdother,
			pceg = pcegn + pcegd,
			pce = pceg + pces,
			gdp = pce + pdi + nx + govt
		)
	
	mDf =
		m$ncpred0$m$base %>%
		dplyr::transmute(
			.,
			date#,
			#psr = ps/pid
		)
	
	m$ncpred1$m$base <<- mDf
	m$ncpred1$q$base <<- qDf
})
```

## Aggregate & calculate display format
```{r}
local({
	
	wide = list()
	
	wide$m$base =
		list(m$ncpred0$m$base, m$ncpred1$m$base) %>%
		purrr::reduce(., function(x, y) dplyr::full_join(x, y, by = 'date')) %>%
		dplyr::arrange(., date)

	wide$q$base =
		list(m$ncpred0$q$base, m$ncpred1$q$base) %>%
		purrr::reduce(., function(x, y) dplyr::full_join(x, y, by = 'date')) %>%
		dplyr::arrange(., date)

	
	wide$m$d1 =
		wide$m$base %>%
		{lapply(colnames(.) %>% .[. != 'date'], function(.varname) {
			
			transform = dplyr::filter(p$variablesDf, varname == .varname)$d1
			fcDf = dplyr::select(., date, .varname) %>% na.omit(.)
			
			histDf = tail(dplyr::filter(na.omit(h$base$m[, c('date', .varname)]), date < min(fcDf$date)), 1)
			
			dplyr::bind_rows(histDf, fcDf) %>%
				dplyr::mutate(
					.,
					!!.varname := 
						{
	                        if (transform == 'apchg') apchg(.[[2]], 12)
							else if (transform == 'pchg') pchg(.[[2]])
							else if (transform == 'base') .[[2]]
							else stop('Err: ', .varname)
							}
						) %>%
				.[2:nrow(.), ]
			
			})} %>%
		purrr::reduce(., function(x, y) dplyr::full_join(x, y, by = 'date')) %>%
		dplyr::arrange(., date)

	
	wide$q$d1 =
		wide$q$base %>%
		{lapply(colnames(.) %>% .[. != 'date'], function(.varname) {
			
			transform = dplyr::filter(p$variablesDf, varname == .varname)$d1
			fcDf = dplyr::select(., date, .varname) %>% na.omit(.)
			
			histDf = tail(dplyr::filter(na.omit(h$base$q[, c('date', .varname)]), date < min(fcDf$date)), 1)
			
			dplyr::bind_rows(histDf, fcDf) %>%
				dplyr::mutate(
					.,
					!!.varname := 
						{
	                        if (transform == 'apchg') apchg(.[[2]], 4)
							else if (transform == 'base') .[[2]]
							else stop('Err: ', .varname)
							}
						) %>%
				.[2:nrow(.), ]
			
			})} %>%
		purrr::reduce(., function(x, y) dplyr::full_join(x, y, by = 'date')) %>%
		dplyr::arrange(., date)

	
	m$ncpred <<- wide
})
```

## Flatten
```{r}
local({
	
	flat =
		m$ncpred %>%
		purrr::imap_dfr(function(x, .freq)
			x %>% purrr::imap_dfr(function(df, .form)
				df %>%
					tidyr::pivot_longer(., -date, names_to = 'varname', values_to = 'value') %>%
					dplyr::mutate(., freq = .freq, form = .form, vdate = p$VINTAGE_DATE)
				)
			) %>%
		na.omit(.)

	m$ncpredFlat <<- flat
})
```


# Finalize

## Export
```{r}
local({
  
    saveRDS(
    	list(p = p, h = h, m = m),
    	str_glue(OUTPUT_DIR, '/[{p$VINTAGE_DATE}] m2.rds')
    	)
    
})
```

