# Set Constants
```{r purl = TRUE}
DIR = 'D:/Onedrive/__Projects/econforecasting'
PACKAGE_DIR = 'D:/Onedrive/__Projects/econforecasting/r-package'
INPUT_DIR = 'D:/Onedrive/__Projects/econforecasting/model-inputs'
OUTPUT_DIR = 'D:/Onedrive/__Projects/econforecasting/model-outputs'
VINTAGE_DATE = '2021-08-23'
```

# Initialize
```{r}
# General purpose
library(tidyverse) # General
library(data.table) # General
library(devtools) # General
library(lubridate) # Dates
library(glue) # String Interpolation
# Data parse/import
library(jsonlite) # JSON Parser
library(rvest) # HTML Parser
library(httr) # CURL Interface
# SQL/Apache Spark
library(DBI) # SQL Interface
# library(RPostgres) # PostgreSQL
# library(rsparklyr) # Spark
# My package
devtools::load_all(path = PACKAGE_DIR)
devtools::document(PACKAGE_DIR)
# library(econforecasting)

# Set working directory
setwd(DIR)

# Read constants
source(file.path(INPUT_DIR, 'constants.r'))
```

## Load RDS
```{r}
local({
	
	rds = readRDS(paste0(OUTPUT_DIR, '/[', VINTAGE_DATE, '] m1.rds'))

	p <<- rds$p
	m <<- rds$m
	h <<- rds$h
})
```


# Nowcast

## Get dates
```{r}
local({
	
	quartersForward = 1
	
	pcaVarnames = p$variablesDf %>% dplyr::filter(., nc_dfm_input == TRUE) %>% .$varname
	
	pcaVariablesDf =
		h$st$m %>%
		dplyr::select(., date, all_of(pcaVarnames)) %>%
		dplyr::filter(., date >= as.Date('2010-01-01'))
	
	bigTDates = pcaVariablesDf %>% dplyr::filter(., !if_any(everything(), is.na)) %>% .$date
	bigTauDates = pcaVariablesDf %>% dplyr::filter(., if_any(everything(), is.na)) %>% .$date
	bigTStarDates =
		bigTauDates %>%
		tail(., 1) %>%
		seq(
			from = .,
			to =
				# Get this quarter
				econforecasting::strdateToDate(paste0(lubridate::year(.), 'Q', lubridate::quarter(.))) %>%
				# Get next quarter minus a month
				lubridate::add_with_rollback(., months(3 * (1 + quartersForward) - 1)),
			by = '1 month'
			) %>%
		.[2:length(.)]
	
	
	bigTDate = tail(bigTDates, 1)
	bigTauDate = tail(bigTauDates, 1)
	bigTStarDate = tail(bigTauDates, 1)
	
	bigT = length(bigTDates)
	bigTau = bigT + length(bigTauDates)
	bigTStar = bigTau + length(bigTStarDates)
	
	timeDf =
		tibble(
			date = as.Date(c(pcaVariablesDf$date[[1]], bigTDate, bigTauDate, bigTStarDate)),
			time = c('1', 'T', 'Tau', 'T*')
		)
	
	

	m$nc$pcaVariablesDf <<- pcaVariablesDf
	m$nc$pcaVarnames <<- pcaVarnames
	m$nc$quartersForward <<- quartersForward
	m$nc$bigTDates <<- bigTDates
	m$nc$bigTauDates <<- bigTauDates
	m$nc$bigTStarDates <<- bigTStarDates
	m$nc$bigTDate <<- bigTDate
	m$nc$bigTauDate <<- bigTauDate
	m$nc$bigTStarDate <<- bigTStarDate
	m$nc$bigT <<- bigT
	m$nc$bigTau <<- bigTau
	m$nc$bigTStar <<- bigTStar
	m$nc$timeDf <<- timeDf
})
```

## Define stack weights
```{r}
local({
	
	bigS = 2
	
	m$nc$bigS <<- bigS
})
```

## Extract factors
```{r}
local({
	
	xDf = m$nc$pcaVariablesDf %>% dplyr::filter(., date %in% m$nc$bigTDates)
	
	xMat =
		xDf %>%
		dplyr::select(., -date) %>%
		as.matrix(.) %>%
		scale(.)
	
	lambdaHat = eigen(t(xMat) %*% xMat) %>% .$vectors
	fHat = (xMat) %*% lambdaHat
	bigN = ncol(xMat)
	bigT = nrow(xMat)
	bigCSquared = min(bigN, bigT)
	
	# Total variance of data
	totalVar = xMat %>% cov(.) %>% diag(.) %>% sum(.)
	
	# Calculate ICs from Bai and Ng (2002)
	# Total SSE should be approx 0 due to normalization above;
	# sapply(1:ncol(xMat), function(i)
	# 	sapply(1:nrow(xMat), function(t)
	# 		(xMat[i, 1] - matrix(lambdaHat[i, ], nrow = 1) %*% matrix(fHat[t, ], ncol = 1))^2
	# 		) %>% sum(.)
	# 	) %>%
	# 	sum(.) %>%
	# 	{./(ncol(xMat) %*% nrow(xMat))}
	(xMat - (fHat %*% t(lambdaHat)))^1
	
	# Now test by R
	mseByR =
		sapply(1:bigN, function(r)
			sum((xMat - (fHat[, 1:r, drop = FALSE] %*% t(lambdaHat)[1:r, , drop = FALSE]))^2)/(bigT * bigN)
			)
	
	
	# Explained variance of data
	screeDf =
		fHat %>% cov(.) %>% diag(.) %>%
		{lapply(1:length(.), function(i)
			tibble(
				factors = i,
				var_explained_by_factor = .[i],
				pct_of_total = .[i]/totalVar,
				cum_pct_of_total = sum(.[1:i])/totalVar
				)
			)} %>%
		dplyr::bind_rows(.) %>%
		dplyr::mutate(., mse = mseByR) %>%
		dplyr::mutate(
			.,
			ic1 = (mse) + factors * (bigN + bigT)/(bigN * bigT) * log((bigN * bigT)/(bigN + bigT)),
			ic2 = (mse) + factors * (bigN + bigT)/(bigN * bigT) * log(bigCSquared),
			ic3 = (mse) + factors * (log(bigCSquared)/bigCSquared)
		)
	
	screePlot =
		screeDf %>%
    	ggplot(.) +
    	geom_col(aes(x = factors, y = cum_pct_of_total, fill = factors)) +
		# geom_col(aes(x = factors, y = pct_of_total)) +
    	labs(title = 'Percent of Variance Explained', x = 'Factors (R)', y = 'Cumulative % of Total Variance Explained', fill = NULL) + 
    	ggthemes::theme_fivethirtyeight()

	
	bigR =
		screeDf %>%
		dplyr::filter(., ic1 == min(ic1)) %>%
		.$factors + 1
		# ((
		# 	{screeDf %>% dplyr::filter(cum_pct_of_total >= .80) %>% head(., 1) %>%.$factors} +
		#   	{screeDf %>% dplyr::filter(., ic1 == min(ic1)) %>% .$factors}
		# 	)/2) %>%
		# round(., digits = 0)
	
	bigRs = seq(from = bigR - 1, by = 1, length.out = m$nc$bigS)
	
	zDfs =
		lapply(bigRs, function(thisR)
			xDf[, 'date'] %>%
			dplyr::bind_cols(
				.,
				fHat[, 1:thisR] %>% as.data.frame(.) %>% setNames(., paste0('f', 1:thisR))
				)
		)
	

	zPlots =
		lapply(zDfs, function(zDf)
			
			purrr::imap(colnames(zDf) %>% .[. != 'date'], function(x, i)
				dplyr::select(zDf, all_of(c('date', x))) %>%
					setNames(., c('date', 'value')) %>%
					ggplot() +
					geom_line(
						aes(x = date, y = value),
						color = hcl(h = seq(15, 375, length = (ncol(zDf) - 1) + 1), l = 65, c = 100)[i] # ncol(zDf) - 1 replaces bigR
						) +
					labs(x = NULL, y = NULL, title = paste0('Estimated PCA Factor ', str_sub(x, -1), ' Plot')) +
					ggthemes::theme_fivethirtyeight() +
					scale_x_date(date_breaks = '1 year', date_labels = '%Y')
				)

			)
	
	factorWeightsDf =
		lambdaHat %>%
		as.data.frame(.) %>% 
		as_tibble(.) %>%
		setNames(., paste0('f', str_pad(1:ncol(.), pad = '0', 1))) %>%
		dplyr::bind_cols(weight = colnames(xMat), .) %>%
		tidyr::pivot_longer(., -weight, names_to = 'varname') %>%
		dplyr::group_by(varname) %>%
		dplyr::arrange(., varname, desc(abs(value))) %>%
		dplyr::mutate(., order = 1:n(), valFormat = paste0(weight, ' (', round(value, 2), ')')) %>%
		dplyr::ungroup(.) %>%
		dplyr::select(., -value, -weight) %>%
		tidyr::pivot_wider(., names_from = varname, values_from = valFormat) %>%
		dplyr::arrange(., order) %>%
		dplyr::select(., -order) %>%
		dplyr::select(., paste0('f', 1:(max(bigRs))))
	
	
	m$nc$factorWeightsDf <<- factorWeightsDf
	m$nc$screeDf <<- screeDf
	m$nc$screePlot <<- screePlot
	m$nc$bigR <<- bigR
	m$nc$pcaInputDf <<- xDf
	
	for (i in 1:m$nc$bigS) {
		m$nc$stack[[i]] <<- list()
		m$nc$stack[[i]]$zDf <<- zDfs[[i]]
		m$nc$stack[[i]]$zPlots <<- zPlots[[i]]
	}
})
```

## Run as VAR(1)
```{r}
local({
	
	varRes = lapply(1:m$nc$bigS, function(i) {
		
		inputDf =
			m$nc$stack[[i]]$zDf %>%
	    	econforecasting::addLags(., 1, TRUE) %>%
			na.omit(.)
		
		yMat = inputDf %>% dplyr::select(., -contains('.l'), -date) %>% as.matrix(.)
		xDf = inputDf %>% dplyr::select(., contains('.l')) %>% dplyr::bind_cols(constant = 1, .)
		
		# solve(t(xMat) %*% xMat) %*% (t(xMat) %*% yMat)
		coefDf =
			lm(yMat ~ . - 1, data = xDf) %>%
			coef(.) %>%
			as.data.frame(.) %>%
			rownames_to_column(., 'coefname') %>%
			as_tibble(.) 
		
		gofDf =
			lm(yMat ~ . - 1, xDf) %>%
			resid(.) %>%
			as.data.frame(.) %>%
			as_tibble(.) %>%
			tidyr::pivot_longer(., everything(), names_to = 'varname') %>%
			dplyr::group_by(., varname) %>%
			dplyr::summarize(., MAE = mean(abs(value)), MSE = mean(value^2))
		residPlot =
			lm(yMat ~ . - 1, xDf) %>%
		    resid(.) %>%
		    as.data.frame(.) %>%
		    as_tibble(.) %>%
		    dplyr::bind_cols(date = inputDf$date, .) %>%
			tidyr::pivot_longer(., -date) %>%
			ggplot(.) + 	
			geom_line(aes(x = date, y = value, group = name, color = name), size = 1) +
			labs(title = 'Residuals plot for PCA factors', x = NULL, y = NULL, color = NULL) +
			ggthemes::theme_fivethirtyeight()
		
		fittedPlots =
			lm(yMat ~ . - 1, data = xDf) %>%
	    	fitted(.) %>%
			as_tibble(.) %>%
			dplyr::bind_cols(date = inputDf$date, ., type = 'Fitted Values') %>%
			dplyr::bind_rows(., m$nc$stack[[i]]$zDf %>% dplyr::mutate(., type = 'Data')) %>%
			tidyr::pivot_longer(., -c('type', 'date')) %>% 
			as.data.table(.) %>%
			split(., by = 'name') %>%
			purrr::imap(., function(x, i)
				ggplot(x) +
					geom_line(
						aes(x = date, y = value, group = type, linetype = type, color = type),
						size = 1, alpha = 1.0
						) +
					labs(
						x = NULL, y = NULL, color = NULL, linetype = NULL,
						title = paste0('Fitted values vs actual for factor ', i)
						) +
					scale_x_date(date_breaks = '1 year', date_labels = '%Y') +
					ggthemes::theme_fivethirtyeight()
				)
		
		bMat = coefDf %>% dplyr::filter(., coefname != 'constant') %>% dplyr::select(., -coefname) %>% t(.)
		cMat = coefDf %>% dplyr::filter(., coefname == 'constant') %>% dplyr::select(., -coefname) %>% t(.)
		qMat =
			lm(yMat ~ . - 1, data = xDf) %>%
		    residuals(.) %>% 
			as_tibble(.) %>%
			purrr::transpose(.) %>%
			lapply(., function(x) as.numeric(x)^2 %>% diag(.)) %>%
			{purrr::reduce(., function(x, y) x + y)/length(.)}
		
		list(
			fittedPlots = fittedPlots,
			residPlot = residPlot,
			gofDf = gofDf,
			coefDf = coefDf,
			qMat = qMat,
			bMat = bMat,
			cMat = cMat
		)
		
	})
	
	
	for (i in 1:m$nc$bigS) {
		m$nc$stack[[i]]$varFittedPlots <<- varRes[[i]]$fittedPlots
		m$nc$stack[[i]]$varResidPlot <<- varRes[[i]]$residPlot
		m$nc$stack[[i]]$varGofDf <<- varRes[[i]]$gofDf
		m$nc$stack[[i]]$varCoefDf <<- varRes[[i]]$coefDf
		m$nc$stack[[i]]$qMat <<- varRes[[i]]$qMat 
		m$nc$stack[[i]]$bMat <<- varRes[[i]]$bMat
		m$nc$stack[[i]]$cMat <<- varRes[[i]]$cMat
	}
})
```


## Run DFM on monthly variables included in PCA
```{r}
local({
	
	
	dfmRes = lapply(1:m$nc$bigS, function(i) {
	
		yMat = m$nc$pcaInputDf %>% dplyr::select(., -date) %>% as.matrix(.)
		xDf = m$nc$stack[[i]]$zDf %>% dplyr::select(., -date) %>% dplyr::bind_cols(constant = 1, .)
		
		coefDf =
			lm(yMat ~ . - 1, xDf) %>%
			coef(.) %>%	
			as.data.frame(.) %>%
	    	rownames_to_column(., 'coefname') %>%
			as_tibble(.)
		
		
		fittedPlots =
			lm(yMat ~ . - 1, xDf) %>%
		    fitted(.) %>%
		    as_tibble(.) %>%
		    dplyr::bind_cols(date = m$nc$stack[[i]]$zDf$date, ., type = 'Fitted Values') %>%
		    dplyr::bind_rows(., m$nc$pcaInputDf %>% dplyr::mutate(., type = 'Data')) %>%
			tidyr::pivot_longer(., -c('type', 'date')) %>%
			as.data.table(.) %>%
			split(., by = 'name') %>%
			purrr::imap(., function(x, i)
	        	ggplot(x) +
		            geom_line(
		                aes(x = date, y = value, group = type, linetype = type, color = type),
		                size = 1, alpha = 1.0
		            ) +
		            labs(
		                x = NULL, y = NULL, color = NULL, linetype = NULL,
		                title = paste0('Fitted values vs actual for factor ', i)
		            ) +
		            scale_x_date(date_breaks = '1 year', date_labels = '%Y') +
		            ggthemes::theme_fivethirtyeight()
		    )
			
		
		gofDf =
			lm(yMat ~ . - 1, xDf) %>%
			resid(.) %>%
			as.data.frame(.) %>%
			as_tibble(.) %>%
			tidyr::pivot_longer(., everything(), names_to = 'varname') %>%
			dplyr::group_by(., varname) %>%
			dplyr::summarize(., MAE = mean(abs(value)), MSE = mean(value^2))
		
		
		aMat = coefDf %>% dplyr::filter(., coefname != 'constant') %>% dplyr::select(., -coefname) %>% t(.)
		dMat = coefDf %>% dplyr::filter(., coefname == 'constant') %>% dplyr::select(., -coefname) %>% t(.)
		rMat0 =
			lm(yMat ~ . - 1, data = xDf) %>%
		    residuals(.) %>% 
			as_tibble(.) %>%
			purrr::transpose(.) %>%
			lapply(., function(x) as.numeric(x)^2 %>% diag(.)) %>%
			{purrr::reduce(., function(x, y) x + y)/length(.)}
		
		rMatDiag = tibble(varname = m$nc$pcaVarnames, variance = diag(rMat0))
		
		rMats =
			lapply(m$nc$bigTauDates, function(d)
				sapply(m$nc$pcaVarnames, function(v)
					h$st$m %>%
						dplyr::filter(., date == (d)) %>%
						.[[v]] %>% 
						{if (is.na(.)) 1e20 else dplyr::filter(rMatDiag, varname == v)$variance}
					) %>%
					diag(.)
				) %>%
			c(lapply(1:length(m$nc$bigTDates), function(x) rMat0), .)
		
		list(
			gofDf = gofDf,
			coefDf = coefDf,
			fittedPlots = fittedPlots,
			rMats = rMats,
			aMat = aMat,
			dMat = dMat
		)
	})
	
	
	for (i in 1:m$nc$bigS) {
		m$nc$stack[[i]]$dfmGofDf <<- dfmRes[[i]]$gofDf
		m$nc$stack[[i]]$dfmCoefDf <<- dfmRes[[i]]$coefDf
		m$nc$stack[[i]]$dfmFittedPlots <<- dfmRes[[i]]$fittedPlots
		m$nc$stack[[i]]$rMats <<- dfmRes[[i]]$rMats
		m$nc$stack[[i]]$aMat <<- dfmRes[[i]]$aMat 
		m$nc$stack[[i]]$dMat <<- dfmRes[[i]]$dMat
	}
})
```


## Compute Kalman filter
```{r}
local({
	
	kfRes = lapply(1:m$nc$bigS, function(i) {

		bMat = m$nc$stack[[i]]$bMat
		cMat = m$nc$stack[[i]]$cMat
		aMat = m$nc$stack[[i]]$aMat
		dMat = m$nc$stack[[i]]$dMat
		rMats = m$nc$stack[[i]]$rMats
		qMat = m$nc$stack[[i]]$qMat
		bigR  = m$nc$bigR + i - 2 # Adjust for stacking - start at bigR - 1
		
		yMats =
			dplyr::bind_rows(
				m$nc$pcaInputDf,
				h$st$m %>%
					dplyr::filter(., date %in% m$nc$bigTauDates) %>%
					dplyr::select(., date, m$nc$pcaVarnames)
				) %>%
			dplyr::mutate(., across(-date, function(x) ifelse(is.na(x), 0, x))) %>%
			dplyr::select(., -date) %>%
			purrr::transpose(.) %>%
			lapply(., function(x) matrix(unlist(x), ncol = 1))
		z0Cond0 = matrix(rep(0, bigR), ncol = 1) # Adjust for stacking
		sigmaZ0Cond0 = matrix(rep(0, bigR^2), ncol = bigR)
			
		zTCondTMinusOne = list()
		zTCondT = list()
		
		sigmaZTCondTMinusOne = list()
		sigmaZTCondT = list()
		
		yTCondTMinusOne = list()
		sigmaYTCondTMinusOne = list()
		
		pT = list()
		for (t in 1:length(c(m$nc$bigTDates, m$nc$bigTauDates))) {
			# message(t)
			# Prediction Step
			zTCondTMinusOne[[t]] = bMat %*% {if (t == 1) z0Cond0 else zTCondT[[t-1]]} + cMat
			sigmaZTCondTMinusOne[[t]] = bMat %*% {if (t == 1) sigmaZ0Cond0 else sigmaZTCondT[[t-1]]} + qMat
			yTCondTMinusOne[[t]] = aMat %*% zTCondTMinusOne[[t]] + dMat
			sigmaYTCondTMinusOne[[t]] = aMat %*% sigmaZTCondTMinusOne[[t]] %*% t(aMat) + rMats[[t]]
			
			# Correction Step
			pT[[t]] = sigmaZTCondTMinusOne[[t]] %*% t(aMat) %*%
				{
					if (t %in% 1:length(m$nc$bigTDates)) solve(sigmaYTCondTMinusOne[[t]])
					else chol2inv(chol(sigmaYTCondTMinusOne[[t]]))
					}
			zTCondT[[t]] = zTCondTMinusOne[[t]] + pT[[t]] %*% (yMats[[t]] - yTCondTMinusOne[[t]])
			sigmaZTCondT[[t]] = sigmaZTCondTMinusOne[[t]] - (pT[[t]] %*% sigmaYTCondTMinusOne[[t]] %*% t(pT[[t]]))
		}
		
		
		kFitted =
			zTCondT %>%
			purrr::map_dfr(., function(x)
				as.data.frame(x) %>% t(.) %>% as_tibble(.)
				) %>%
			dplyr::bind_cols(date = c(m$nc$bigTDates, m$nc$bigTauDates), .) 
		
		
		## Smoothing step
		zTCondBigTSmooth = list()
		sigmaZTCondBigTSmooth = list()
		sT = list()
		
		for (t in (length(zTCondT) - 1): 1) {
			# message(t)
			sT[[t]] = sigmaZTCondT[[t]] %*% t(bMat) %*% solve(sigmaZTCondTMinusOne[[t + 1]])
			zTCondBigTSmooth[[t]] = zTCondT[[t]] + sT[[t]] %*% 
				({if (t == length(zTCondT) - 1) zTCondT[[t + 1]] else zTCondBigTSmooth[[t + 1]]} - zTCondTMinusOne[[t + 1]])
			sigmaZTCondBigTSmooth[[t]] = sigmaZTCondT[[t]] - sT[[t]] %*%
				(sigmaZTCondTMinusOne[[t + 1]] -
				 	{if (t == length(zTCondT) - 1) sigmaZTCondT[[t + 1]] else sigmaZTCondBigTSmooth[[t + 1]]}
				 ) %*% t(sT[[t]])
		}
		
		kSmooth =
			zTCondBigTSmooth %>%
			purrr::map_dfr(., function(x)
				as.data.frame(x) %>% t(.) %>% as_tibble(.)
				) %>%
			dplyr::bind_cols(date = c(m$nc$bigTDates, m$nc$bigTauDates) %>% .[1:(length(.) - 1)], .) 
		
		
		
		
		## Forecasting step
		zTCondBigT = list()
		sigmaZTCondBigT = list()
		yTCondBigT = list()
		sigmaYTCondBigT = list()
		
		for (j in 1:length(m$nc$bigTStarDates)) {
			zTCondBigT[[j]] = bMat %*% {if (j == 1) zTCondT[[length(zTCondT)]] else zTCondBigT[[j - 1]]} + cMat
			sigmaZTCondBigT[[j]] = bMat %*% {if (j == 1) sigmaZTCondT[[length(sigmaZTCondT)]] else sigmaZTCondBigT[[j - 1]]} + qMat
			yTCondBigT[[j]] = aMat %*% zTCondBigT[[j]] + dMat
			sigmaYTCondBigT[[j]] = aMat %*% sigmaZTCondBigT[[j]] %*% t(aMat) + rMats[[1]]
		}
		
		kForecast =
			zTCondBigT %>%
			purrr::map_dfr(., function(x)
				as.data.frame(x) %>% t(.) %>% as_tibble(.)
				) %>%
			dplyr::bind_cols(date = m$nc$bigTStarDates, .) # %>% dplyr::mutate(., f1 = 0) # mean(dplyr::filter(m$nc$zDf, date < '2020-03-01')$f1))
		
		
		# Plot and Cleaning
		kfPlots =
			lapply(colnames(m$nc$stack[[i]]$zDf) %>% .[. != 'date'], function(.varname)
				dplyr::bind_rows(
					dplyr::mutate(m$nc$stack[[i]]$zDf, type = 'Data'),
					dplyr::mutate(kFitted, type = 'Kalman Filtered'),
					dplyr::mutate(kForecast, type = 'Forecast'),
					dplyr::mutate(kSmooth, type = 'Kalman Smoothed'),
					) %>%
					tidyr::pivot_longer(., -c('date', 'type'), names_to = 'varname') %>%
					dplyr::filter(., varname == .varname) %>%
					ggplot(.) +
					geom_line(aes(x = date, y = value, color = type), size = 1) + 
					labs(x = NULL, y = NULL, color = NULL, title = paste0('Kalman smoothed values for ', .varname)) +
		            scale_x_date(date_breaks = '1 year', date_labels = '%Y') +
					ggthemes::theme_fivethirtyeight()
				)
		
		
		fDf =
			dplyr::bind_rows(
				kSmooth,
				tail(kFitted, 1),
				kForecast
				)
		
		yDf =
			yTCondBigT %>%
			purrr::map_dfr(., function(x) as_tibble(t(as.data.frame(x)))) %>%
			dplyr::bind_cols(date = m$nc$bigTStarDates, .)
		
		kfDf = yDf
			# yDf %>%
			# dplyr::select(
			# 	.,
			# 	date#,
			# 	#all_of(dplyr::filter(m$paramsDf, nowcast == 'kf')$varname)
			# 	)
		
		
		fPlot =
			fDf %>%
			tidyr::pivot_longer(., -date) %>%
			dplyr::filter(., date >= as.Date('2018-01-01')) %>%
			ggplot(.) +
			geom_line(aes(x = date, y = value, color = name)) +
			geom_vline(aes(xintercept = m$nc$bigTDate), linetype = 'dotted') +
			labs(title = NULL, x = NULL, y = NULL, color = NULL) + facet_wrap( ~ name) +
			ggthemes::theme_economist()
		
		list(
			fDf = fDf,
			fPlot = fPlot,
			kfPlots = kfPlots,
			yDf = yDf,
			kfDf = kfDf
		)
		
	})
	
	
	
	for (i in 1:m$nc$bigS) {
		m$nc$stack[[i]]$fDf <<- kfRes[[i]]$fDf
		m$nc$stack[[i]]$kfPlots <<- kfRes[[i]]$kfPlots
		m$nc$stack[[i]]$yDf <<- kfRes[[i]]$yDf
		m$nc$stack[[i]]$kfDf <<- kfRes[[i]]$kfDf
	}
})
```


# Model Stacking

## Forecast dfm.m monthly variables
```{r}
local({
	
	dfmVarnames = p$variablesDf %>% dplyr::filter(., nc_method == 'dfm.m') %>% .$varname
	
	dfmMDfs = lapply(1:m$nc$bigS, function(i) {
		lapply(dfmVarnames, function(.varname) {
			inputDf =
				dplyr::inner_join(
					m$nc$stack[[i]]$fDf,
					dplyr::select(h$st$m, date, all_of(.varname)),
					by = 'date'
				) %>%
				na.omit(.)

			yMat = dplyr::select(inputDf, all_of(.varname)) %>% as.matrix(.)
			xDf = dplyr::select(inputDf, -date, -all_of(.varname)) %>% dplyr::mutate(., constant = 1)

			coefDf =
				lm(yMat ~ . - 1, xDf)$coef %>%
	    		as.data.frame(.) %>% rownames_to_column(., 'coefname')	%>% as_tibble(.) %>%
				setNames(., c('coefname', 'value'))

			# Forecast dates + last historical date
			forecastDf0 =
				tibble(
					date = seq(from = tail(inputDf$date, 1), to = tail(m$nc$bigTStarDates, 1), by = '1 month')
					) %>%
				.[2:nrow(.), ] %>%
				dplyr::mutate(., !!.varname := 0) %>%
				dplyr::left_join(., m$nc$stack[[i]]$fDf, by = 'date') %>%
				dplyr::bind_cols(., constant = 1)

			forecastDf =
				purrr::reduce(1:nrow(forecastDf0), function(accum, x) {
					accum[x, .varname] =
						accum[x, ] %>%
						dplyr::select(., coefDf$coefname) %>%
						matrix(., ncol = 1) %>%
						{matrix(coefDf$value, nrow = 1) %*% as.numeric(.)}

					return(accum)
				}, .init = forecastDf0) %>%
				dplyr::select(., all_of(c('date', .varname)))
# 
# 			inputDf =
# 				dplyr::inner_join(
# 				m$nc$fDf,
# 				dplyr::select(m$h$m$st, date, all_of(.varname)) %>%
# 					econforecasting::addLags(., 1, .zero = TRUE),
# 				by = 'date'
# 				) %>%
# 				na.omit(.)
# 			
# 			yMat = dplyr::select(inputDf, all_of(.varname)) %>% as.matrix(.)
# 			xDf = dplyr::select(inputDf, -date, -all_of(.varname)) %>% dplyr::mutate(., constant = 1)
# 			
# 			coefDf =
# 				lm(yMat ~ . - 1, xDf)$coef %>%
# 	    		as.data.frame(.) %>% rownames_to_column(., 'coefname')	%>% as_tibble(.) %>%
# 				setNames(., c('coefname', 'value'))
# 			
# 			# Forecast dates + last historical date
# 			forecastDf0 =
# 				tibble(
# 					date = seq(from = tail(inputDf$date, 1), to = tail(m$nc$bigTStarDates, 1), by = '1 month')
# 					) %>%
# 				dplyr::mutate(., !!.varname := c(inputDf[[paste0(.varname, '.l1')]][[1]], rep(NA, nrow(.) - 1))) %>%
# 				dplyr::left_join(., m$nc$fDf, by = 'date') %>%
# 				dplyr::bind_cols(., constant = 1)
# 			
# 			forecastDf =
# 				purrr::reduce(2:nrow(forecastDf0), function(accum, x) {
# 					accum[x, .varname] =
# 						accum %>% econforecasting::addLags(., 1, .zero = TRUE) %>%
# 						.[x, ] %>%
# 						dplyr::select(., coefDf$coefname) %>%
# 						matrix(., ncol = 1) %>%
# 						{matrix(coefDf$value, nrow = 1) %*% as.numeric(.)}
# 					
# 					return(accum)
# 				}, .init = forecastDf0) %>%
# 				.[2:nrow(.), ] %>%
# 				dplyr::select(., all_of(c('date', .varname)))
		
			}) %>%
			purrr::reduce(., function(accum, x) dplyr::full_join(accum, x, by = 'date')) %>%
			dplyr::arrange(., date)
	})
	
	
	# Stack models - take sample mean of all models
	dfmMDf =
		dfmMDfs %>%
		purrr::imap_dfr(., function(x, i)
			tidyr::pivot_longer(x, -date, names_to = 'varname', values_to = paste0('value'), values_drop_na = TRUE)
			) %>%
		dplyr::group_by(., date, varname) %>%
		dplyr::summarize(., value = mean(value), .groups = 'drop') %>%
		tidyr::pivot_wider(., names_from = varname, values_from = value) %>%
		dplyr::arrange(., date)


	for (i in 1:m$nc$bigS) {
		m$nc$stack[[i]]$dfmMDf <<- dfmMDfs[[i]]
	}
	m$nc$dfmMDf <<- dfmMDf	
})
```

## Forecast dfm.q quarterly variables w/elastic net
```{r}
local({
	
	dfmVarnames = p$variablesDf %>% dplyr::filter(., nc_method == 'dfm.q') %>% .$varname
	
	
	res = lapply(1:m$nc$bigS, function(i) {
		message('Fitting elastic net ... ', i)
		fDf =
			m$nc$stack[[i]]$fDf %>%
			tidyr::pivot_longer(., -date, names_to = 'varname') %>%
			dplyr::mutate(
				.,
				q = econforecasting::strdateToDate(paste0(lubridate::year(date), 'Q', lubridate::quarter(date)))
				) %>%
			dplyr::select(., -date) %>%
			dplyr::group_by(., varname, q) %>%
			dplyr::summarize(., value = mean(value), .groups = 'drop') %>%
			tidyr::pivot_wider(., names_from = varname, values_from = value) %>%
			dplyr::rename(., date = q)
		
		
		dfmRes =
			lapply(dfmVarnames %>% setNames(., .), function(.varname) {
		# 		inputDf =
		# 			dplyr::inner_join(
		# 				fDf,
		# 				dplyr::select(m$h$q$st, date, all_of(.varname)),
		# 				by = 'date'
		# 			) %>%
		# 			na.omit(.)
		# 
		# 		yMat = dplyr::select(inputDf, all_of(.varname)) %>% as.matrix(.)
		# 		xDf = dplyr::select(inputDf, -date, -all_of(.varname)) %>% dplyr::mutate(., constant = 1)
		# 
		# 		coefDf =
		# 			lm(yMat ~ . - 1, xDf)$coef %>%
		#     		as.data.frame(.) %>% rownames_to_column(., 'coefname')	%>% as_tibble(.) %>%
		# 			setNames(., c('coefname', 'value'))
		# 
		# 		# Forecast dates + last historical date
		# 		forecastDf0 =
		# 			tibble(
		# 				date = seq(from = tail(inputDf$date, 1), to = tail(m$nc$bigTStarDates, 1), by = '3 months')
		# 				) %>%
		# 			.[2:nrow(.), ] %>%
		# 			dplyr::mutate(., !!.varname := 0) %>%
		# 			dplyr::left_join(., m$nc$fDf, by = 'date') %>%
		# 			dplyr::bind_cols(., constant = 1)
		# 
		# 		forecastDf =
		# 			purrr::reduce(1:nrow(forecastDf0), function(accum, x) {
		# 				accum[x, .varname] =
		# 					accum[x, ] %>%
		# 					dplyr::select(., coefDf$coefname) %>%
		# 					matrix(., ncol = 1) %>%
		# 					{matrix(coefDf$value, nrow = 1) %*% as.numeric(.)}
		# 
		# 				return(accum)
		# 			}, .init = forecastDf0) %>%
		# 			dplyr::select(., all_of(c('date', .varname)))
	
				inputDf =
					dplyr::inner_join(
						fDf,
						dplyr::select(h$st$q, date, all_of(.varname)) %>%
							econforecasting::addLags(., 1, .zero = TRUE),
						    # dplyr::mutate(., !!paste0('lma.', .varname) := econforecasting::lma(.[[.varname]], 2)),
						by = 'date'
					) %>%
					na.omit(.)
	
				yMat = dplyr::select(inputDf, all_of(.varname)) %>% as.matrix(.)
				xDf = dplyr::select(inputDf, -date, -all_of(.varname)) %>% dplyr::mutate(., constant = 1)
				
				glmResult = lapply(seq(from = 0, to = 1.0, by = 0.10), function(.alpha) {
					cv =
						glmnet::cv.glmnet(
							x = xDf %>% dplyr::select(., -constant) %>% as.matrix(.),
							y = yMat,
							deviance = 'mae',
							alpha = .alpha,
							intercept = TRUE
						)
					tibble(alpha = .alpha, lambda = cv$lambda, mae = cv$cvm) %>%
					dplyr::mutate(., min_lambda_for_given_alpha = (mae == min(mae))) %>%
					return(.)
					}) %>%
					dplyr::bind_rows(.) %>%
					dplyr::mutate(., min_overall = (mae == min(mae)))
	
				glmOptim = glmResult %>% dplyr::filter(., min_overall == TRUE)
	
				cvPlot =
					glmResult %>%
					ggplot(.) +
					geom_line(aes(x = log(lambda), y = mae, group = alpha, color = alpha)) +
					geom_point(
						data = glmResult %>% dplyr::filter(., min_lambda_for_given_alpha == TRUE),
						aes(x = log(lambda), y = mae), color = 'red'
					) +
					geom_point(
						data = glmResult %>% dplyr::filter(., min_overall == TRUE),
						aes(x = log(lambda), y = mae), color = 'green'
					) +
					labs(
						x = 'log(Lambda)', y = 'MAE', color = 'alpha',
						title = 'Elastic Net Hyperparameter Fit',
						subtitle = 'Red = MAE Minimizing Lambda for Given Alpha;
						Green = MAE Minimizing (Lambda, Alpha) Pair'
						)
				
			
				glmObj =
					glmnet::glmnet(
						x = xDf %>% dplyr::select(., -constant) %>% as.matrix(.),
						y = yMat,
						alpha = glmOptim$alpha,
						lambda = glmOptim$lambda
					)
	  
				coefMat = glmObj %>% coef(.) %>% as.matrix(.)
				
				coefDf =
					coefMat %>%
				    as.data.frame(.) %>%
				    rownames_to_column(., var = 'Covariate') %>%
				    setNames(., c('coefname', 'value')) %>%
					as_tibble(.) %>%
					dplyr::mutate(., coefname = ifelse(coefname == '(Intercept)', 'constant', coefname))
	
				
				# Standard OLS
		# 		coefDf =
		# 			lm(yMat ~ . - 1, xDf)$coef %>%
		#     		as.data.frame(.) %>% rownames_to_column(., 'coefname') %>% as_tibble(.) %>%
		# 			setNames(., c('coefname', 'value'))
	
				# Forecast dates + last historical date
				forecastDf0 =
					tibble(
						date = seq(from = head(tail(inputDf$date, 2), 1), to = tail(m$nc$bigTStarDates, 1), by = '3 months')
						# date = seq(from = tail(inputDf$date, 1), to = tail(m$nc$bigTStarDates, 1), by = '3 months')
						) %>%
					# dplyr::mutate(., !!.varname := c(tail(inputDf[[.varname]], 1), rep(NA, nrow(.) - 1))) %>%
					dplyr::mutate(., !!.varname := c(tail(inputDf[[.varname]], 2), rep(NA, nrow(.) - 2))) %>%
					dplyr::left_join(., m$nc$stack[[i]]$fDf, by = 'date') %>%
					dplyr::bind_cols(., constant = 1)
	
				forecastDf =
					purrr::reduce((2 + 1):nrow(forecastDf0), function(accum, x) {
						accum[x, .varname] =
							accum %>%
							econforecasting::addLags(., 2, .zero = TRUE) %>%
						    # dplyr::mutate(., !!paste0('lma.', .varname) := econforecasting::lma(.[[.varname]], 1)) %>%
							.[x, ] %>%
							dplyr::select(., coefDf$coefname) %>%
							matrix(., ncol = 1) %>%
							{matrix(coefDf$value, nrow = 1) %*% as.numeric(.)}
	
						return(accum)
					}, .init = forecastDf0) %>%
					.[(2 + 1):nrow(.), ] %>%
					dplyr::select(., all_of(c('date', .varname)))
				
				list(
					forecastDf = forecastDf,
					coefDf = coefDf,
					glmOptim = glmOptim,
					cvPlot = cvPlot
					)
				})
		
		
		glmCoefList = purrr::map(dfmRes, ~ .$coefDf) 
		
		glmOptimDf =
			purrr::imap_dfr(dfmRes, function(x, i)
				x$glmOptim %>% dplyr::bind_cols(varname = i, .)
				)
		
		cvPlots = purrr::map(dfmRes, ~ .$cvPlot)
	
		dfmQDf =
			dfmRes %>%
			lapply(., function(x) x$forecastDf) %>%
			purrr::reduce(., function(accum, x) dplyr::full_join(accum, x, by = 'date')) %>%
			dplyr::arrange(., date)
		
		list(
			glmCoefList = glmCoefList,
			glmOptimDf = glmOptimDf,
			cvPlots = cvPlots,
			dfmQDf = dfmQDf
		)
	})

	
	dfmQDf = 
		res %>%
		purrr::imap_dfr(., function(x, i)
			tidyr::pivot_longer(x$dfmQDf, -date, names_to = 'varname', values_to = paste0('value'), values_drop_na = TRUE)
			) %>%
		dplyr::group_by(., date, varname) %>%
		dplyr::summarize(., value = mean(value), .groups = 'drop') %>%
		tidyr::pivot_wider(., names_from = varname, values_from = value) %>%
		dplyr::arrange(., date)

	
	for (i in 1:m$nc$bigS) {
		m$nc$stack[[i]]$glmCoefQList <<- res[[i]]$glmCoefList 
		m$nc$stack[[i]]$glmOptimQDf <<- res[[i]]$glmOptimDf
		m$nc$stack[[i]]$cvPlotsQ <<- res[[i]]$cvPlots
		m$nc$stack[[i]]$dfmQDf <<- res[[i]]$dfmQDf
	}
	m$nc$dfmQDf <<- dfmQDf
})
```


# Finalize Nowcasts

## Aggregate
```{r}
local({
	
	mDf = m$nc$dfmMDf
		# list(m$nc$dfmMDf, m$nc$cmefiDf) %>%
		# purrr::reduce(., function(x, y) dplyr::full_join(x, y, by = 'date')) %>%
		# dplyr::arrange(., date)
	
	qDf =
		list(m$nc$dfmQDf) %>%
		purrr::reduce(., function(x, y) dplyr::full_join(x, y, by = 'date')) %>%
		dplyr::arrange(., date)


	m$ncpred0$st$m <<- mDf
	m$ncpred0$st$q <<- qDf
})
```


## Detransform
```{r}
local({
	
		
	mDf =
		m$ncpred0$st$m %>%
		{lapply(colnames(.) %>% .[. != 'date'], function(.varname) {
			
			transform = dplyr::filter(p$variablesDf, varname == .varname)$st
			
			fcDf = dplyr::select(., date, .varname) %>% na.omit(.)
				
			histDf = tail(dplyr::filter(na.omit(h$base$m[, c('date', .varname)]), date < min(fcDf$date)), 1)
			
			fcDf %>%
				dplyr::mutate(
					.,
					!!.varname := 
						{
	                        if (transform == 'dlog') undlog(fcDf[[2]], histDf[[2]])
							else if (transform == 'apchg') unapchg(fcDf[[2]], 12, histDf[[2]])
							else if (transform == 'base') .[[2]]
							else stop('Err: ', .varname)
							}
						)
			
			})} %>%
		purrr::reduce(., function(x, y) dplyr::full_join(x, y, by = 'date')) %>%
		dplyr::arrange(., date)
	
	
	qDf =
		m$ncpred0$st$q %>%
		{lapply(colnames(.) %>% .[. != 'date'], function(.varname) {
			
			transform = dplyr::filter(p$variablesDf, varname == .varname)$st
			
			fcDf = dplyr::select(., date, .varname) %>% na.omit(.)
				
			histDf = tail(dplyr::filter(na.omit(h$base$q[, c('date', .varname)]), date < min(fcDf$date)), 1)
			
			fcDf %>%
				dplyr::mutate(
					.,
					!!.varname := 
						{
	                        if (transform == 'dlog') undlog(fcDf[[2]], histDf[[2]])
							else if (transform == 'apchg') unapchg(fcDf[[2]], 4, histDf[[2]])
							else if (transform == 'base') .[[2]]
							else stop('Err: ', .varname)
							}
						)
			
			})} %>%
		purrr::reduce(., function(x, y) dplyr::full_join(x, y, by = 'date')) %>%
		dplyr::arrange(., date)
		
	
	m$ncpred0$base$m <<- mDf
	m$ncpred0$base$q <<- qDf
})
```

## D1 Form
```{r}
local({
	
	res = lapply(list('d1') %>% setNames(., .), function(.form) {
		
		mDf =
			m$ncpred0$base$m %>%
			{lapply(colnames(.) %>% .[. != 'date'], function(.varname) {
				
				transform = dplyr::filter(p$variablesDf, varname == .varname)[[.form]]
				fcDf = dplyr::select(., date, .varname) %>% na.omit(.)
				histDf = tail(dplyr::filter(na.omit(h$base$m[, c('date', .varname)]), date < min(fcDf$date)), 1)
				
				dplyr::bind_rows(histDf, fcDf) %>%
					dplyr::mutate(
						.,
						!!.varname := 
							{
		                        if (transform == 'dlog') dlog(.[[2]])
								else if (transform == 'apchg') apchg(.[[2]], 12)
								else if (transform == 'pchg') pchg(.[[2]])
								else if (transform == 'base') .[[2]]
								else stop('Err: ', .varname)
								}
							) %>% .[2:nrow(.),]
				
				})} %>%
			purrr::reduce(., function(x, y) dplyr::full_join(x, y, by = 'date')) %>%
			dplyr::arrange(., date)
		
		
		qDf =
			m$ncpred0$base$q %>%
			{lapply(colnames(.) %>% .[. != 'date'], function(.varname) {
				
				transform = dplyr::filter(p$variablesDf, varname == .varname)$st
				fcDf = dplyr::select(., date, .varname) %>% na.omit(.)
				histDf = tail(dplyr::filter(na.omit(h$base$q[, c('date', .varname)]), date < min(fcDf$date)), 1)
				
				dplyr::bind_rows(histDf, fcDf) %>%
					dplyr::mutate(
						.,
						!!.varname := 
							{
		                        if (transform == 'dlog') dlog(.[[2]])
								else if (transform == 'apchg') apchg(.[[2]], 4)
								else if (transform == 'pchg') pchg(.[[2]])
								else if (transform == 'base') .[[2]]
								else stop('Err: ', .varname)
								}
							) %>% .[2:nrow(.),]
				
				})} %>%
			purrr::reduce(., function(x, y) dplyr::full_join(x, y, by = 'date')) %>%
			dplyr::arrange(., date)
		
		list(m = mDf, q = qDf)
	})
	

	
	for (.form in names(res)) {
		m$ncpred0[[.form]] <<- res[[.form]]
	}
})
```


## Calculate GDP nowcast
```{r}
local({
	
	qDf =
		m$ncpred0$base$q %>%
		dplyr::transmute(
			.,
			date,
			govt = govtf + govts,
			ex = exg + exs,
			im = img + ims,
			nx = ex - im,
			pdin = pdinstruct + pdinequip + pdinip,
			pdi = pdin + pdir + pceschange,
			pces = pceshousing + pceshealth + pcestransport + pcesrec + pcesfood + pcesfinal + pcesother + pcesnonprofit,
			pcegn = pcegnfood + pcegnclothing + pcegngas + pcegnother,
			pcegd = pcegdmotor + pcegdfurnish + pcegdrec + pcegdother,
			pceg = pcegn + pcegd,
			pce = pceg + pces,
			gdp = pce + pdi + nx + govt
		)
	
	mDf =
		m$ncpred0$base$m %>%
		dplyr::transmute(
			.,
			date,
			psr = ps/pid
		)
	
	m$ncpred1$base$m <<- mDf
	m$ncpred1$base$q <<- qDf
})
```

## Aggregate & calculate display format
```{r}
local({
	
	wide1 = list()
	
	wide1$base$m =
		list(m$ncpred0$base$m, m$ncpred1$base$m) %>%
		purrr::reduce(., function(x, y) dplyr::full_join(x, y, by = 'date')) %>%
		dplyr::arrange(., date)

	wide1$base$q =
		list(m$ncpred0$base$q, m$ncpred1$base$q) %>%
		purrr::reduce(., function(x, y) dplyr::full_join(x, y, by = 'date')) %>%
		dplyr::arrange(., date)
	
	

	wide2 = lapply(list('st', 'd1', 'd2') %>% setNames(., .), function(.form) {
		mDf =
			wide1$base$m %>%
			{lapply(colnames(.) %>% .[. != 'date'], function(.varname) {
				
				transform = dplyr::filter(p$variablesDf, varname == .varname)[[.form]]
				fcDf = dplyr::select(., date, .varname) %>% na.omit(.)
				histDf = tail(dplyr::filter(na.omit(h$base$m[, c('date', .varname)]), date < min(fcDf$date)), 1)
				
				dplyr::bind_rows(histDf, fcDf) %>%
					dplyr::mutate(
						.,
						!!.varname := 
							{
		                        if (transform == 'dlog') dlog(.[[2]])
								else if (transform == 'apchg') apchg(.[[2]], 12)
								else if (transform == 'pchg') pchg(.[[2]])
								else if (transform == 'base') .[[2]]
								else if (transform == 'none') NA
								else stop('Err: ', .varname)
								}
							) %>% .[2:nrow(.),]
				
				})} %>%
			purrr::keep(., function(x) !all(is.na(x[[2]]))) %>% # Cull nones
			purrr::reduce(., function(x, y) dplyr::full_join(x, y, by = 'date')) %>%
			dplyr::arrange(., date)
		
		
		qDf =
			wide1$base$q %>%
			{lapply(colnames(.) %>% .[. != 'date'], function(.varname) {
				
				transform = dplyr::filter(p$variablesDf, varname == .varname)[[.form]]
				fcDf = dplyr::select(., date, .varname) %>% na.omit(.)
				histDf = tail(dplyr::filter(na.omit(h$base$q[, c('date', .varname)]), date < min(fcDf$date)), 1)
				
				dplyr::bind_rows(histDf, fcDf) %>%
					dplyr::mutate(
						.,
						!!.varname := 
							{
		                        if (transform == 'dlog') dlog(.[[2]])
								else if (transform == 'apchg') apchg(.[[2]], 4)
								else if (transform == 'pchg') pchg(.[[2]])
								else if (transform == 'base') .[[2]]
								else if (transform == 'none') NA
								else stop('Err: ', .varname)
								}
							) %>% .[2:nrow(.),]
				
				})} %>%
			purrr::keep(., function(x) !all(is.na(x[[2]]))) %>% # Cull nones
			purrr::reduce(., function(x, y) dplyr::full_join(x, y, by = 'date')) %>%
			dplyr::arrange(., date)
		
		list(m = mDf, q = qDf)
	})
	
	
	wide = c(wide1, wide2)

	
	m$ncpred <<- wide
})
```

## Flatten
```{r}
local({
	
	flat =
		m$ncpred %>%
		purrr::imap_dfr(function(x, .form)
			x %>% purrr::imap_dfr(function(df, .freq)
				df %>%
					tidyr::pivot_longer(., -date, names_to = 'varname', values_to = 'value') %>%
					dplyr::mutate(., freq = .freq, form = .form, vdate = p$VINTAGE_DATE)
				)
			) %>%
		na.omit(.)

	m$ncpredFlat <<- flat
})
```


# Finalize

## Export
```{r}
local({
  
    saveRDS(
    	list(p = p, h = h, m = m),
    	str_glue(OUTPUT_DIR, '/[{p$VINTAGE_DATE}] m2.rds')
    	)
    
})
```

