# Set Constants
```{r purl = TRUE}
DIR = 'D:/Onedrive/__Projects/econforecasting'
PACKAGE_DIR = 'D:/Onedrive/__Projects/econforecasting/r-package'
INPUT_DIR = 'D:/Onedrive/__Projects/econforecasting/model-inputs'
OUTPUT_DIR = 'D:/Onedrive/__Projects/econforecasting/model-outputs'
VINTAGE_DATE = '2021-08-27'
```

# Initialize
```{r}
# General purpose
library(tidyverse) # General
library(data.table) # General
library(devtools) # General
library(lubridate) # Dates
library(glue) # String Interpolation
# Data parse/import
library(jsonlite) # JSON Parser
library(rvest) # HTML Parser
library(httr) # CURL Interface
# Visualization
library(ggpmisc) # Tables
library(cowplot) # Join ggplots
# SQL/Apache Spark
library(DBI) # SQL Interface
# library(RPostgres) # PostgreSQL
# library(rsparklyr) # Spark
# My package
devtools::load_all(path = PACKAGE_DIR)
devtools::document(PACKAGE_DIR)
# library(econforecasting)

# Set working directory
setwd(DIR)

# Read constants
source(file.path(INPUT_DIR, 'constants.r'))
```

## Load RDS
```{r}
local({
	
	rds = readRDS(paste0(OUTPUT_DIR, '/[', VINTAGE_DATE, '] m3.rds'))

	p <<- rds$p
	m <<- rds$m
	h <<- rds$h
})
```


# CSM Estimation

## Get Exogenous Df
```{r}
local({
	
	# Get exogenous df - combine historical for all variables with forecasts from qual
	# There should be no overlap but if so, overwrites historical from qual
	exogDfs =
		m$qual$predFlat %>%
		as.data.table(.) %>%
		split(., by = 'scenarioname', keep.by = FALSE) %>%
		lapply(., function(forecastDf)
			dplyr::full_join(
				forecastDf %>% as_tibble(.) %>% dplyr::rename(., qual = value),
				h$flat %>% dplyr::transmute(., form, freq, varname, date, hist = value),
				by = c('form', 'freq', 'varname', 'date')
				) %>%
				dplyr::transmute(., form, freq, varname, date, value = ifelse(!is.na(hist), hist, qual)) %>%
				as.data.table(.) %>%
				split(., by = c('form', 'freq'), keep.by = FALSE, flatten = FALSE) %>%
				lapply(., function(y)
					lapply(y, function(z)
						z %>%
							tidyr::pivot_wider(., names_from = 'varname', values_from = 'value') %>%
							dplyr::arrange(., date)
						)
					)
			)
	
	
	exogFlat = 
		exogDfs %>% 
		purrr::imap_dfr(., function(x, .scenarioname)
			purrr::imap_dfr(x, function(y, .form)
				purrr::imap_dfr(y, function(z, .freq)
					z %>%
						tidyr::pivot_longer(-date, values_to = 'value', names_to = 'varname') %>%
						dplyr::mutate(., freq = .freq)
					) %>%
					dplyr::mutate(., form = .form)
				) %>%
				dplyr::mutate(., scenarioname = .scenarioname)
			)
	
	
	m$csm$exogDfs <<- exogDfs
	m$csm$exogFlat <<- exogFlat
})
```


## Forecast Periods
```{r}
local({
	
	# Pull start date by finding the first date where at least one CORE.ENDOG variables is non-empty
	startDate =
		m$csm$exogDfs$baseline$st$q %>%
		dplyr::select(., date, dplyr::filter(p$variablesDf, core_structural == 'core.endog')$varname) %>%
		dplyr::filter(., date >= as.Date('2020-01-01')) %>%
		tidyr::pivot_longer(., -date, names_to = 'varname') %>%
	    dplyr::mutate(., isNa = ifelse(is.na(value), 1, 0)) %>%
	    dplyr::group_by(., date) %>%
	    dplyr::summarize(., countNa = sum(isNa), .groups = 'drop') %>%
		dplyr::filter(., countNa > 0) %>%
		dplyr::arrange(., date) %>%
		head(., 1) %>%
		.$date
	
	
	# # Pull end date by last date of CORE.EXOG variables
	endDate =
		m$csm$exogDfs$baseline$st$q %>%
	    dplyr::select(., date, dplyr::filter(p$variablesDf, core_structural == 'core.exog')$varname) %>%
	    dplyr::filter(., date >= as.Date('2020-01-01')) %>%
	    tidyr::pivot_longer(., -date, names_to = 'varname') %>%
	    dplyr::mutate(., isNa = ifelse(is.na(value), 1, 0)) %>%
	    dplyr::group_by(., date) %>%
	    dplyr::summarize(., countNa = sum(isNa), .groups = 'drop') %>%
	    dplyr::filter(., countNa == 0) %>%
	    dplyr::arrange(., date) %>%
	    tail(., 1) %>%
	    .$date
	
	# Let end date be 10 years after the start date
	# endDate = lubridate::add_with_rollback(startDate, years(5))
	
	m$csm$startDate <<- startDate
	m$csm$endDate <<- endDate
})
```

## Identity Equations
```{r}
local({
	
    # Get steady-state values
    ss =
        h$base$q %>%
        na.omit(.) %>%
        dplyr::filter(., date == max(date)) %>%
        dplyr::select(., -date) %>%
    	tidyr::pivot_longer(everything(), names_to = 'varname')

    identityLlEquations = c(
    	'gdp = pce + pdi + ex - im + govt',
    	'pce = pceg + pces',
    	'pceg = pcegd + pcegn',
		'pcegd = pcegdmotor + pcegdfurnish + pcegdrec + pcegdother',
		'pcegn = pcegnfood + pcegnclothing + pcegngas + pcegnother',
		'pces = pceshousing + pceshealth + pcestransport + pcesrec + pcesfood + pcesfinal + pcesother + pcesnonprofit',
		'pdin = pdinstruct + pdinequip + pdinip',
		'ex = exg + exs',
		'im = img + ims',
		'govt = govtf + govts'
    )
    
    
    # identityEqns = c(
    # )

    
    coefMatsIdentity =
    	lapply(identityLlEquations, function(eqn) {
    		
	        yCoef = eqn %>% str_split_fixed(., '=', 2) %>% .[1, 1] %>% str_squish(.)
	        
	        xCoefs =
	            eqn %>%
	            str_split_fixed(., '=', 2) %>%
	            .[1, 2] %>%
	        	# Split by whitespace following by a plus or minus
	        	# https://stackoverflow.com/a/50650318
    			str_split(., '\\s+(?=\\+|-)') %>%
	        	.[[1]] %>%
	            str_replace_all(., ' ', '')
	        
    		res =
    			tibble(
    				varname = xCoefs,
    				rhsDenom = filter(ss, varname == yCoef)$value
    				) %>%
    			dplyr::mutate(
    				.,
    				multiplier = ifelse(str_sub(varname, 1, 1) == '-', -1, 1),
    				varname =
    					ifelse(str_sub(varname, 1, 1) == '-', str_sub(varname, 2),
    						   ifelse(str_sub(varname, 1, 1) == '+', str_sub(varname, 2),
    						   	   varname
    						   	   ))
    				) %>%
    			dplyr::left_join(., transmute(ss, varname, rhsNum = value), by = c('varname')) %>%
    			dplyr::transmute(., varname, coef = -1 * multiplier * rhsNum/rhsDenom) %>%
    			{
    				if (any(is.na(.$coef))) stop('Error!')
    				else .
    			} %>%
    			dplyr::bind_rows(tibble(varname = yCoef, coef = 1), .) %>%
    			tidyr::pivot_wider(., names_from = 'varname', values_from = 'coef')
    		}) %>%
    	setNames(., map(., ~ colnames(.)[1]))

	
    # Verify that all equations marked with identity or identity.ll have been calculated
	p$variablesDf %>% 
    	filter(., core_endog_type %in% c('identity', 'identity.ll')) %>%
		.$varname %>%
		sort(.) %>%
		{. == sort(names(coefMatsIdentity))} %>%
		{
			if (!all(.)) stop('Mismatch')
			else message('Identity equations checked OK')
			}

	m$csm$coefMatsIdentity <<- coefMatsIdentity
})
```

## Estimate Coefficients
```{r}
local({
	
	# Get historical data for training
	histDf =
		h$st$q %>%
		dplyr::filter(., date < m$csm$startDate)
	

    histDfAll =
        histDf %>%
        dplyr::bind_cols(
            .,
            constant = 1,
            dplyr::transmute_if(histDf, is.numeric, function(x) ma2(x)) %>%
                dplyr::rename_with(., function(x) paste0('ma2.', x)),

            dplyr::transmute_if(histDf, is.numeric, function(x) lma2(x)) %>%
                dplyr::rename_with(., function(x) paste0('lma2.', x)),
            
            dplyr::transmute_if(histDf, is.numeric, function(x) wma2(x)) %>%
                dplyr::rename_with(., function(x) paste0('wma2.', x)),
            
            dplyr::transmute_if(histDf, is.numeric, function(x) wma4(x)) %>%
                dplyr::rename_with(., function(x) paste0('wma4.', x)),


            lapply(1:4, function(l)
                dplyr::transmute_if(histDf, is.numeric, function(x) dplyr::lag(x, l)) %>%
                    dplyr::rename_with(., function(x) paste0(x, '.l', l))
                )
            )

    # Iterate through equations
    eqnsList = list(
    	'pcegdmotor = constant + wma4.pid + ma2.ue + lma2.pcegdmotor + oil',
    	'pcegdfurnish = constant + wma4.pid + ma2.ue + lma2.pcegdfurnish',
    	'pcegdrec = constant + wma4.pid + ma2.ue + lma2.pcegdrec',
    	'pcegdother = constant + wma4.pid + ma2.ue + lma2.pcegdother',
    	'pcegnfood = constant + wma4.pid + ma2.ue + lma2.pcegnfood',
    	'pcegnclothing = constant + wma4.pid + ma2.ue + lma2.pcegnclothing',
    	'pcegngas = constant + wma4.pid + ma2.ue + lma2.pcegngas',
    	'pcegnother = constant + wma4.pid + ma2.ue + lma2.pcegnother',
    	'pceshousing = constant + wma4.pid + ma2.ue + lma2.pceshousing',
    	'pceshealth = constant + wma4.pid + ma2.ue + lma2.pceshealth',
    	'pcestransport = constant + wma4.pid + ma2.ue + lma2.pcestransport',
    	'pcesrec = constant + wma4.pid + ma2.ue + lma2.pcesrec',
    	'pcesfood = constant + wma4.pid + ma2.ue + lma2.pcesfood',
    	'pcesfinal = constant + wma4.pid + ma2.ue + lma2.pcesfinal',
    	'pcesother = constant + wma4.pid + ma2.ue + lma2.pcesother',
    	'pcesnonprofit = constant + wma4.pid + ma2.ue + lma2.pcesnonprofit',
    	
    	'pdi = constant + pdin + pdir',
    	'pdinstruct = constant + wma2.pce + ue + spy + lma2.pdinstruct + wma2.t10y',
    	'pdinequip = constant + wma2.pce + ue + spy + lma2.pdinequip + wma2.t10y',
    	'pdinip = constant + wma2.pce + ue + spy + lma2.pdinip + wma2.t10y',
    	'pdir = constant + wma2.pce + ue + spy + lma2.pdir + wma2.mort30y + wma2.hpi',

    	'exg = constant + lma2.pdin + lma2.exg',
        'exs = constant + lma2.pdin + lma2.exs',
        'img = constant + lma2.pdin + lma2.img',
        'ims = constant + lma2.pdin + lma2.ims',
    	
        'govtf = constant + govtf.l1 + lma2.gdp',
        'govts = constant + govts.l1 + lma2.gdp',

        'houst = constant + hpi + lma2.ue + mort30y + lma2.hsold',
        'hsold = constant + hpi + lma2.ue + mort30y + lma2.houst',
        'hpermits = constant + hpi + lma2.ue + mort30y + lma2.hpermits',
    	
    	'vsales = constant + pce + oil',
    	'emp = constant + ue + gdp',
    	'jolts = constant + ue + gdp',
    	
    	'oil = constant + lma2.oil + spy + hpi',
    	
    	'delinqrer = constant + ma2.ue + ma2.pid + lma2.delinqrer',
    	'delinqcc = constant + ma2.ue + ma2.pid + lma2.delinqcc',
    	'delinqci = constant + ma2.ue + ma2.pid + lma2.delinqci',

    	'mort5y = constant + mort30y',

        'vix = constant + vix.l1 + spy + spy.l1',
        'moo = constant + moo.l1 + spy + gdp',
        'metals = constant + metals.l1 + spy + gdp'
        )

    # Get estimated coefficient matrices
    estimRes = purrr::map(eqnsList, function(eqn) {
    	
        message(eqn)
        
        yCoef = eqn %>% str_split_fixed(., '=', 2) %>% .[1, 1] %>% str_squish(.)
        
        xCoefs =
            eqn %>%
            str_split_fixed(., '=', 2) %>%
            .[1, 2] %>%
            str_split(., '\\+') %>%
            .[[1]] %>%
            str_squish(.)
        	
        inputDf =
            histDfAll %>%
            dplyr::select(., date, all_of(c(yCoef, xCoefs))) %>%
            na.omit(.)
        
        yMat = inputDf %>% dplyr::select(., all_of(yCoef)) %>% as.matrix(.)
        xMat = inputDf %>% dplyr::select(., all_of(xCoefs)) %>% as.matrix(.)
        
        lmObj = lm(yMat ~ . - 1, data = as_tibble(xMat))
    	gofStats =
    		lmObj %>% broom::glance(.) %>%
    		dplyr::transmute(., varname = yCoef, r2 = r.squared, adjr2 = adj.r.squared, aic = AIC, bic = BIC, p = p.value)
    	
        gofCoefStats =
        	lmObj %>% broom::tidy(.)
        
        ##### Replace lma2.pceg coefficients with pceg.l1, pceg.l2 etc
        # stop()
        
        coefRes =
            solve(t(xMat) %*% xMat) %*% (t(xMat) %*% yMat) %>%
            as.data.frame(.) %>%
            rownames_to_column(.) %>%
            setNames(., c('coefname', 'value')) %>%
            as_tibble(.) %>%
        	purrr::transpose(.) %>%
        	purrr::map_dfr(., function(x) {
        		
        		if (str_sub(x$coefname, 1, 5) == 'lma2.') {
        			coefname = paste0(str_sub(x$coefname, 6), c('.l1', '.l2'))
        			value = x$value * .5
        		} else if (str_sub(x$coefname, 1, 4) == 'ma2.') {
        			coefname = paste0(str_sub(x$coefname, 5), c('', '.l1'))
        			value = x$value * .5
        		} else if (str_sub(x$coefname, 1, 5) == 'wma2.') {
        			coefname = paste0(str_sub(x$coefname, 6), c('', '.l1'))
        			value = x$value * getWmaWeights(2)
        		} else if (str_sub(x$coefname, 1, 5) == 'wma4.') {
        			coefname = paste0(str_sub(x$coefname, 6), c('', '.l1', '.l2', '.l3'))
        			value = x$value * getWmaWeights(4)
        		} else {
        			coefname = x$coefname
        			value = x$value
        		}
        		
        		tibble(coefname = coefname, value = value)
        	}) %>%
            dplyr::transmute(., coefname, value = value * -1) %>%
            dplyr::bind_rows(tibble(coefname = yCoef, value = 1), .) %>%
            tidyr::pivot_wider(., names_from = 'coefname')
        
        fittedPlot =
        	tibble(date = inputDf$date, hist = yMat[, 1], fitted = fitted(lmObj)) %>%
        	tidyr::pivot_longer(., -date) %>%
        	ggplot(.) +
        	geom_line(aes(x = date, y = value, color = name)) +
        	labs(title = yCoef, x = NULL, y = NULL)
        
        return(list(
        	lmObj = lmObj,
        	fittedPlot = fittedPlot,
        	gofCoefStats = gofCoefStats,
        	gofStats = gofStats,
        	coefRes = coefRes,
        	varname = yCoef
        ))
    }) %>% setNames(., map(., ~ .$varname))
    
    
    estimRegs = map(estimRes, ~ .$lmObj)
    estimFittedPlots = map(estimRes, ~ .$fittedPlots)
    estimGofStats = map_dfr(estimRes, ~ .$gofStats)
    coefMatsEstimated = map(estimRes,  ~ .$coefRes)
    
    
    # Verify that all equations list match exactly with that specified in inputs.xlsx
	list(
	    tibble(a = sort(filter(p$variablesDf, core_endog_type %in% c('estimated'))$varname)),
		tibble(a = sort(names(coefMatsEstimated)))
		) %>%
		{waldo::compare(.[[1]], .[[2]])}
		# {c(
		# 	nrow(anti_join(.[[1]], .[[2]], by = 'a')),
		# 	nrow(anti_join(.[[2]], .[[1]], by = 'a'))
		# 	)} %>%
		# {if (!all(. == 0)) stop('Mismatch') else message('Estimated equations checked OK')}

	

    m$csm$estimRegs <<- estimRegs
    m$csm$estimFittedPlots <<- estimFittedPlots
    m$csm$estimGofStats <<- estimGofStats
    m$csm$coefMatsEstimated <<- coefMatsEstimated
})
```

## Join Coefficient Matrices
```{r}
local({
	
    coefMat =
        purrr::imap_dfr(c(m$csm$coefMatsIdentity, m$csm$coefMatsEstimated), function(x, i)
        	dplyr::bind_cols(coefname = i, x)
        	) %>%
        replace(., is.na(.), 0)
    
    
	# Seperate endog (estimated) and exogenous variables -> NOTE there may be some overlap 
    # Partially exogenous variables will be in both the endogVars and exogVars matrices
    endogVars = names(c(m$csm$coefMatsIdentity, m$csm$coefMatsEstimated))
    exogVars = p$variablesDf %>% dplyr::filter(., core_structural == 'core.exog') %>% .$varname
	
	m$csm$coefMat <<- coefMat
	m$csm$endogVars <<- endogVars
	m$csm$exogVars <<- exogVars
})
```

# CSM Forecasts

## CSM Forecasts - Quarterly
```{r}
local({
    
	coefMat = m$csm$coefMat

	forecasts = lapply(m$csm$exogDfs, function(exogScenarioDf) {
		
	    # Create exog df - start 4 quarters before forecast start date
	    exogDf =
			exogScenarioDf$st$q %>%
	    	dplyr::filter(., date >= lubridate::add_with_rollback(m$csm$startDate, months(-12)) & date <= m$csm$endDate)
	
	
	    # Pass accumulator new exogenous variables each time
	    resDf = purrr::reduce(5:nrow(exogDf), function(df, .row) {
	        
	        allCoefDf =
	            df %>%
	            dplyr::bind_cols(
	                .,
	                constant = 1,
	                lapply(1:4, function(l)
	                    dplyr::transmute_if(df, is.numeric, function(x) dplyr::lag(x, l)) %>%
	                        dplyr::rename_with(., function(x) paste0(x, '.l', l))
	                    )
	                ) %>%
	            dplyr::select(., c('date', colnames(coefMat) %>% .[. != 'coefname'])) %>%
	            .[.row, ]
	        
	        
	        bMatVars = allCoefDf %>% tidyr::pivot_longer(., -date) %>% dplyr::filter(., is.na(value)) %>% .$name
	        dMatVars = allCoefDf %>% tidyr::pivot_longer(., -date) %>% dplyr::filter(., !is.na(value)) %>% .$name
	        # Only keep equations where not already filled
	        cMat =
	        	coefMat %>% dplyr::filter(., coefname %in% bMatVars) %>% dplyr::select(., all_of(dMatVars)) %>% as.matrix(.) %>%
	        	{. * -1}
	        aMat = coefMat %>% dplyr::filter(., coefname %in% bMatVars) %>% dplyr::select(., all_of(bMatVars)) %>% as.matrix(.)
	        dMat = allCoefDf %>% dplyr::select(., all_of(dMatVars)) %>% as.matrix(.) %>% t(.)
	        
	        bMat = solve(aMat) %*% (cMat %*% dMat)
	        bMatVec = bMat %>% as.data.frame(.) %>% rownames_to_column(.) %>% {setNames(.$V1, .$rowname)}
	        
	        for (varname in names(bMatVec)) {
	            df[[.row, varname]] = bMatVec[[varname]]
	        }
	        
	        return(df)
	    }, .init = exogDf)
	    
	    
	    pred =
	    	resDf %>%
	    	dplyr::filter(., date >= m$csm$startDate) %>%
	    	dplyr::select(., all_of(c('date', m$csm$endogVars, m$csm$exogVars)))

	})
	
	
    m$csm$predst <<- forecasts
})
```


## Convert to Base
```{r}
local({

	res =
		m$csm$predst %>%
		lapply(., function(df)
			lapply(colnames(df) %>% .[. != 'date'], function(.varname) {
			
				transform = dplyr::filter(p$variablesDf, varname == .varname)$st
				fcDf = dplyr::select(df, date, .varname) %>% na.omit(.)
				histDf = tail(dplyr::filter(na.omit(h$base$q[, c('date', .varname)]), date < min(fcDf$date)), 1)
				
				fcDf %>%
					dplyr::mutate(
						.,
						!!.varname := 
							{
		                        if (transform == 'dlog') undlog(fcDf[[2]], histDf[[2]])
								else if (transform == 'apchg') unapchg(fcDf[[2]], 4, histDf[[2]])
								else if (transform == 'diff1') undiff(fcDf[[2]], 1, histDf[[2]])
								else if (transform == 'pchg') unpchg(fcDf[[2]], histDf[[2]])
								else if (transform == 'base') .[[2]]
								else stop('Err: ', .varname)
								}
							)
				
				}) %>%
			purrr::reduce(., function(x, y) dplyr::full_join(x, y, by = 'date')) %>%
			dplyr::arrange(., date)
		)

	m$csm$predbase0 <<- res
})
```


## Forecast Monthly Variables
```{r}
local({

	# Delete quarterly forecasts on quarters where monthly data exists ->
	# replace with monthly forecasts and interpolate with remaining monthly forecasts

	predbase0m = imap(m$csm$predbase0, function(df, scenarioname) {
		
		varnames =
			p$variablesDf %>%
			dplyr::filter(core_structural %in% c('core.endog', 'core.exog.p') & freq %in% c('d', 'w', 'm')) %>%
			.$varname

		lapply(varnames, function(.varname) {
			message(.varname)
			df %>%
				dplyr::transmute(., date, csm = .[[.varname]]) %>% # Shift back by one quarter to middle of quarter
				mutate(., date = add_with_rollback(date, months(1))) %>%
				dplyr::left_join(
					tibble(
						date =
							seq(
								from = add_with_rollback(head(.$date, 1), months(-4)),
								to = add_with_rollback(tail(.$date, 1), months(1)),
								by = '1 month'
								)
						),
					.,
					by = 'date'
					) %>%
				dplyr::left_join(
					.,
					h$base$m %>% dplyr::transmute(., date, hist = .[[.varname]]),
					by = 'date'
					) %>%
				dplyr::mutate(., value = ifelse(!is.na(hist), hist, csm)) %>%
				dplyr::mutate(., value = zoo::na.spline(value)) %>%
				dplyr::transmute(., date, !!.varname := value)

			}) %>%
			purrr::reduce(., function(x, y) dplyr::full_join(x, y, by = 'date')) %>%
			# Bind qualitative variables for calculations
			dplyr::left_join(., m$qual$pred[[scenarioname]]$base$m, by = 'date') %>%
			dplyr::arrange(., date) %>%
			# Calculations
			# dplyr::mutate(
			# 	.,
			# 	ps = pid - po,
			# 	psr = ps/pi
			# ) %>%
			# Now get columns to show only if after historical data
			{lapply(colnames(.) %>% .[. != 'date'], function(varname)
				dplyr::select(., all_of(c('date', varname))) %>%
					dplyr::filter(., date > max(na.omit(h$base$m[, c('date', varname)])$date))
			)} %>%
			purrr::reduce(., function(x, y) dplyr::full_join(x, y, by = 'date'))
		})
	
	
	m$csm$predbase0m <<- predbase0m
})
```

## Reaggregate to Quartlery & Add Identity
```{r}
local({
	
	# Aggregate monthly variables to quarterly and replace existing quarterly variables in m$csm$predbase0
	res = imap(m$csm$predbase0m, function(df, scenarioname)
		
		# First need to bind to historical variables in case needed for quarterly aggregation
		df %>%
			tidyr::pivot_longer(., -date, names_to = 'varname', values_to = 'value', values_drop_na = TRUE) %>%
			dplyr::group_by(., varname) %>%
			namedSplit(.) %>%
		    imap(., function(x, .varname)
		    	x %>%
		    		dplyr::bind_rows(
		    			dplyr::filter(h$flat, date < x$date[[1]] & varname == .varname & freq == 'm' & form == 'base')[, c('date', 'varname', 'value')],
		                .
		                ) %>%
		    	 	na.omit(.) %>%
		    	 	econforecasting::monthlyDfToQuarterlyDf(.) %>%
		    	 	dplyr::filter(., date > tail(na.omit(h$base$q[, c('date', .varname)]), 1)$date) %>%
		    		set_names(., c('date', .varname))
		    	) %>%
			purrr::reduce(., function(x, y) full_join(x, y, by = 'date')) %>%
			dplyr::arrange(., date) %>%
			# Now replace existing quarterly variables in m$csm$predbase0
			tidyr::pivot_longer(., -date, names_to = 'varname', values_to = 'value', values_drop_na = TRUE) %>%
			dplyr::full_join(
				.,
				tidyr::pivot_longer(m$csm$predbase0[[scenarioname]], -date, names_to = 'varname', values_to = 'value_prev', values_drop_na = TRUE),
				by = c('date', 'varname')
				) %>%
			dplyr::transmute(
				.,
				date,
				varname,
				value = ifelse(!is.na(value), value, value_prev)
			) %>%
			tidyr::pivot_wider(., names_from = 'varname', values_from = 'value') %>%
			dplyr::arrange(., date) %>%
			# Finally add calculated variables
			dplyr::mutate(
				.,
				nx = ex - im
			)
		) 

	
	m$csm$predbaseq <<- res
})
```


# Model Stacking

## Monthly (convert to stationary form then aggregate) 
```{r}
local({
	
	# Combine with nowcasts and external forecasts
	# Merge external from SPF
	
	
})
```


## Quarterly
```{r}
local({
	
	# Convert all to monthly, then deaggregate
	
	# flat0 =
	# 	dplyr::bind_rows(
	# 		purrr::imap_dfr(m$csm$predbaseq, function(x, i)
	# 			tidyr::pivot_longer(x, -date, names_to = 'varname', values_drop_na = TRUE) %>%
	# 				dplyr::mutate(., freq = 'q', scenarioname = i, form = 'base')
	# 			),
	# 		purrr::imap_dfr(m$csm$predbase0m, function(x, i)
	# 			tidyr::pivot_longer(x, -date, names_to = 'varname', values_drop_na = TRUE) %>%
	# 				dplyr::mutate(., freq = 'm', scenarioname = i, form = 'base')
	# 			)
	# 		) %>%
	# 	dplyr::group_by(., freq, scenarioname, form, varname) %>%
	# 	dplyr::group_split(.) %>%
	# 	lapply(., function(x) {
	# 		
	# 		.varname = x$varname[[1]]
	# 		.freq = x$freq[[1]]
	# 		.scenarioname = x$scenarioname[[1]]
	# 		
	# 		transform = dplyr::filter(p$variablesDf, varname == .varname)[['st']]
	# 		fcDf = dplyr::select(x, date, value) %>% na.omit(.)
	# 		histDf =
	# 			dplyr::filter(na.omit(p$variables[[.varname]]$h[['st']][[.freq]]), date < min(fcDf$date)) %>%
	# 			tail(., 1) %>%
	# 			dplyr::select(., date, value)
	# 			
	# 		dplyr::bind_rows(histDf, fcDf) %>%
	# 			dplyr::mutate(
	# 				.,
	# 				value = 
	# 					{
	#                         if (transform == 'dlog') dlog(.[[2]])
	# 						else if (transform == 'apchg') apchg(.[[2]], 12)
	# 						else if (transform == 'pchg') pchg(.[[2]])
	# 						else if (transform == 'base') .[[2]]
	# 						else if (transform == 'none') NA
	# 						else stop('Err: ', .varname)
	# 						}
	# 					) %>%
	# 			.[2:nrow(.),] %>%
	# 			dplyr::mutate(
	# 				.,
	# 				scenarioname = .scenarioname,
	# 				varname = .varname,
	# 				freq = .freq
	# 			)
	# 	})

})
```


# Final Aggregation 

## Transform 
```{r}
local({
	
	flatBase =
		dplyr::bind_rows(
			purrr::imap_dfr(m$csm$predbaseq, function(x, i)
				tidyr::pivot_longer(x, -date, names_to = 'varname', values_drop_na = TRUE) %>%
					dplyr::mutate(., freq = 'q', scenarioname = i, form = 'base')
				),
			purrr::imap_dfr(m$csm$predbase0m, function(x, i)
				tidyr::pivot_longer(x, -date, names_to = 'varname', values_drop_na = TRUE) %>%
					dplyr::mutate(., freq = 'm', scenarioname = i, form = 'base')
				)
			)

	flat =
		flatBase %>%
		dplyr::group_by(., freq, scenarioname, form, varname) %>%
		dplyr::group_split(.) %>%
		purrr::imap_dfr(., function(x, i) {
			# message(i)
			.varname = x$varname[[1]]
			.freq = x$freq[[1]]
			.scenarioname = x$scenarioname[[1]]

			fcDf = dplyr::select(x, date, value) %>% na.omit(.)
			histDf =
				dplyr::filter(na.omit(p$variables[[.varname]]$h[['base']][[.freq]]), date < min(fcDf$date)) %>%
				tail(., 1) %>%
				dplyr::select(., date, value)
			
			purrr::map_dfr(c('d1', 'd2'), function(.form) {
				
				transform = dplyr::filter(p$variablesDf, varname == .varname)[[.form]]

				dplyr::bind_rows(histDf, fcDf) %>%
					dplyr::mutate(
						.,
						value = 
							{
		                        if (transform == 'dlog') dlog(.[[2]])
								else if (transform == 'apchg') apchg(.[[2]], {if (.freq == 'q') 4 else 12})
								else if (transform == 'pchg') pchg(.[[2]])
								else if (transform == 'base') .[[2]]
								else if (transform == 'none') NA
								else stop('Err: ', .varname)
								}
							) %>%
					.[2:nrow(.),] %>%
					dplyr::mutate(
						.,
						scenarioname = .scenarioname,
						varname = .varname,
						freq = .freq,
						form = .form
					)
			}) %>% na.omit(.)
		}) %>%
		dplyr::bind_rows(flatBase, .)
	
	
	
	res =
		flat %>%
		as.data.table(.) %>% 
		split(., by = c('scenarioname', 'freq', 'form'), flatten = FALSE, keep.by = FALSE) %>%
		lapply(., function(x)
			lapply(x, function(y)
				lapply(y, function(z)
					as_tibble(z) %>%
						tidyr::pivot_wider(., names_from = 'varname', values_from = 'value') %>%
						dplyr::arrange(., date)
					)
				)
			)
	
	
	for (scenarioname in names(res)) {
		m$csm$pred[[scenarioname]] <<- res[[scenarioname]]
	}
	m$csm$predFlat <<- flat
})
```

## Plot
```{r}
local({
	
	predCharts =
		m$csm$predFlat %>%
		dplyr::group_by(., varname) %>%
		econforecasting::namedSplit(.) %>%
		lapply(., function(x) {
			
			message(x$varname[[1]])
			param =
				p$variablesDf %>%
				dplyr::filter(., varname == x$varname[[1]]) %>%
				as.list(.)
			
			plots =
				purrr::cross(list(freq = c('q', 'm'), form = c('d1', 'd2'))) %>%
				setNames(., map_chr(., ~ paste0(.$form, '.', .$freq))) %>%
				lapply(., function(y) {
					
					if (y$freq == 'm' && param$freq == 'q') return(NULL)
					if (param[[y$form]] == 'none') return(NULL)
					
					# message(y$form, ';', y$freq)
					
					transform = param[[y$form]]
					unitname = {
						if (transform == 'apchg') 'Annualized % Chg'
						else if (transform == 'pchg') 'Pct Chg'
						else if (transform == 'dlog') 'Log-Difference'
						else if (transform == 'base') param$units
						else if (transform == 'none') 'None'
						else stop ('Add transform type')
					}
					
					histDf = 
						h$flat %>%
						dplyr::filter(., freq == y$freq, form == y$form, varname == param$varname) %>%
						dplyr::arrange(., date) %>%
						dplyr::transmute(., date, value, type = 'historical')

					forecastDf =
						x %>%
						dplyr::filter(., freq == y$freq & form == y$form) %>%
						dplyr::bind_rows(mutate(tail(histDf, 1), scenarioname = unique(.$scenarioname)), .) %>%
						dplyr::transmute(., date, value, type = scenarioname)
					
					dplyr::bind_rows(histDf, forecastDf) %>%
						ggplot(.) +
						geom_line(aes(x = date, y = value, color = type)) +
						geom_point(aes(x = date, y = value, color = type)) +
						scale_color_manual(
							values = c('historical' = 'black', 'baseline' = 'red')
						) +
						scale_linetype_manual(
							values = c('historical' = 'solid', 'baseline' = 'solid')
						) +
						geom_table(
							data = tibble(
								x = max(forecastDf$date),
								y = max(bind_rows(histDf, forecastDf)$value),
					            z = list(
					            	forecastDf %>%
					            		mutate(., value = round(value, 1)) %>%
					            		pivot_wider(., names_from = 'type', values_from = 'value') %>%
					            		arrange(., date) %>%
					            		.[1:4, ]
					            	)
							),
							aes(x = x, y = y, label = z),
							size = 2
							) +
						labs(
							subtitle = paste0({if (y$freq == 'q') 'Quarterly' else 'Monthly'}, ' Forecast'),
							x = NULL, y = unitname, color = NULL, linetype = NULL
							) +
						theme_gray(base_size = 12) +
						theme(axis.title = element_text(size = 10), axis.title.y = element_text(size = 10))
					}) %>%
				purrr::keep(., ~ !is.null(.) && nrow(.$data) > 0)

			title =
				cowplot::ggdraw() +
				cowplot::draw_label(param$fullname, fontface = 'bold', x = 0, hjust = 0) +
				theme(plot.margin = margin(0, 0, 0, 20))
			
			
			col1 =  {
				if (!is.null(plots$d1.q) && !is.null(plots$d2.q))
					cowplot::plot_grid(
						plots$d1.q + theme(legend.position = 'none'),
						plots$d2.q + theme(legend.position = 'none'),
						ncol = 1,
						rel_heights = c(1, .8)
						)
				else if (!is.null(plots$d1.q))
					cowplot::plot_grid(plots$d1.q + theme(legend.position = 'none'), ncol = 1)
				else
					NULL
				}
					
			col2 =  {
				if (!is.null(plots$d1.m) && !is.null(plots$d2.m))
					cowplot::plot_grid(
						plots$d1.m + theme(legend.position = 'none'),
						plots$d2.m + theme(legend.position = 'none'),
						ncol = 1,
						rel_heights = c(1, .8)
						)
				else if (!is.null(plots$d1.m))
					cowplot::plot_grid(plots$d1.m + theme(legend.position = 'none'), ncol = 1)
				else
					NULL
			}
			
			plotArea = {
				if (!is.null(col1) && !is.null(col2)) cowplot::plot_grid(col1, col2, nrow = 1)
				else if (!is.null(col1)) cowplot::plot_grid(col1, nrow = 1)
				else stop('None')
			}
			
			cowplot::plot_grid(
				title,
				plotArea,
				cowplot::get_legend(plots[[1]] + guides(color = guide_legend(nrow = 1))),
				nrow = 3,
				rel_heights = c(.15, 1, .1)
			)
			

			})
	
	print(predCharts)
	
	purrr::imap(predCharts, function(x, i)
		ggsave(
			file.path(OUTPUT_DIR, paste0('csm_', i, '.png')),
			plot = x, scale = 2.5, width = 4, height = 3, units = 'in'
			)
		)
	
	
	m$csm$predCharts <<- predCharts
})
```

# Finalize

## Export
```{r}
local({
  
    saveRDS(
    	list(p = p, h = h, m = m),
    	str_glue(OUTPUT_DIR, '/[{p$VINTAGE_DATE}] m4.rds')
    	)
    
})
```

